### 2020-05-13 Functions/RT_Plots.Rmd
Establish repo for analysis

---
title: "RT Plots"
author: "Patrick Skippen"
date: "09/03/2020"
output: pdf_document
---

The following pages display plots desribing the RT effects on Modality, Preparation, Distraction, and Pain Condition. Headers seperate these specific effects. Pay attention to the key of each plot to determine the split of data (i.e., Distractor; Present vs. Absent).

```{r Load Data, message=FALSE, warning=FALSE, include=FALSE}
load("../Output/RT_Plots.RData")
```

# Modaility Effects
```{r Modality, echo=FALSE, message=FALSE, warning=FALSE}
Plots$Modality[["Accuracy"]]
Plots$Modality[["Preparation"]]
Plots$Modality[["Distraction"]]
Plots$Modality[["Condition"]]
```

# Preparation Effects
```{r Preparation, echo=FALSE, message=FALSE, warning=FALSE}
Plots$Preparation[["Accuracy"]]
Plots$Preparation[["Modality"]]
Plots$Preparation[["Distraction"]]
Plots$Preparation[["Condition"]]
```

# Distraction Effects
```{r Distraction, echo=FALSE, message=FALSE, warning=FALSE}
Plots$Distraction[["Accuracy"]]
Plots$Distraction[["Modality"]]
Plots$Distraction[["Preparation"]]
Plots$Distraction[["Condition"]]
```

# Condition Effects
```{r Condition, echo=FALSE, message=FALSE, warning=FALSE}
Plots$Condition[["Accuracy"]]
Plots$Condition[["Modality"]]
Plots$Condition[["Preparation"]]
Plots$Condition[["Distraction"]]
```

### 2020-05-13 ManuscriptMarkdown.Rmd
Establish repo for analysis

---
title             : "Cross frequency coupling of attentional EEG task under pain"
shorttitle        : "Cross Pain"
author: 
  - name          : "Patrick Skippen"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Neuroscience Research Australia, Barker St, Randwick, Australia"
    email         : "p.skippen@neura.edu.au"
  - name          : "David Seminowicz"
    affiliation   : "1"
  - name          : "Ali Mazaheri"
    affiliation   : "2"
  - name          : "Samantha Mallard"
    affiliation   : "1"
  - name          : "Siobhan Schabrun"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Neuroscience Research Australia, Randwick Australia"
  - id            : "2"
    institution   : "Where-ever Ali is, Country"
author_note: |

  Author's  contributions: DS and AM conceptualised the research plan and rationale. PS took the lead role in manuscript preparation, formulated the analysis plan, and undertook majority of the data analysis. SS xyz.
  The data and code used to create this manuscript can be found at https://osf.io/XXXX/
  This is version 1: 02/2020
abstract: |
  blah blah.

keywords          : ""
bibliography      : "r-references.bib"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
draft             : no
lang              : "english"
class             : "man"
output            :
  papaja::apa6_pdf:
    latex_engine: xelatex
header-includes: #allows you to add in your own Latex packages
- \usepackage{float} #use the 'float' package
- \usepackage{caption}
- \floatplacement{figure}{H} #make every figure with caption = h
- \raggedbottom
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
editor_options: 
  chunk_output_type: console
---

\setlength{\abovedisplayskip}{-20pt}
\setlength{\belowdisplayskip}{3pt}
\setlength{\abovedisplayshortskip}{-30pt}
\setlength{\belowdisplayshortskip}{3pt}

```{r Packages and Libraries, message = FALSE, warning = FALSE, echo = FALSE}
# installs packages if necessary - MUST locate packages before knitting
.libPaths("./Packages")
Packages <- c("ggplot2","dplyr","reshape",#"wesanderson",
              "BayesFactor",
              "kableExtra","rmatio","Rmisc",
              "rmarkdown","data.table","devtools") # Slew of packages used here.

# # Install CRAN packages, if necessary
if(sum(!Packages %in% rownames(installed.packages()))>=1){
invisible(lapply(Packages,install.packages,dependencies=TRUE))
}

# Library Packags
invisible(lapply(Packages,library,character.only=TRUE))

## Standard error function
stderr <- function(x, na.rm=FALSE) {
  if (na.rm) x <- na.omit(x)
  sqrt(var(x)/length(x))
}
## Formatting Number Function for tables and output
numformat <- function(x, digits = 2) { 
    ncode <- paste0("%.", digits, "f")
    sub("^(-?)0.", "\\1.", sprintf(ncode, x))
}

# Install Git Packages, if necessary
if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")
# if(!"wordcountaddin" %in% rownames(installed.packages())) devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)

# References info
papaja::r_refs(file = "r-references.bib")

# Knitting options
knitr::opts_chunk$set(comment = NA)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = TRUE, fig.pos= "h")
```

# 1. Introduction

# 2. Methods
```{r Methods Set-up, echo=FALSE}
Subjidx <- dir("../Data/")
# Participant "CLP130" has a few problems. Including odd trigger codes. We'll rid ourselves of this participant for now.
Subjidx <- Subjidx[-30]

Conditions <- c("np","p")
source('Functions/ExtractRT_MATLAB.R')

## Below code only runs the first time. If Output/Trial_list exsits it will simply load the data.
if(!file.exists("Output/Trial_list.RData")){
Trial.list <- list()
## Extract Trial.list
for(px in seq_along(Subjidx)){
  Trial.list[["np"]][[px]] <- ExtractTrialData(PartID = Subjidx[px],COND = "np")

}
names(Trial.list[["np"]]) <- Subjidx

# N.B - CLP116 is missing pain data
Subjidx_p <- Subjidx[-16]
for (px in seq_along(Subjidx)) {
  if (file.exists(paste(
    "../Data/",
    Subjidx[px],
    "/Behaviour/",
    paste(Subjidx[px], "p", sep = "_"),
    "_EventCodes.mat",
    sep = ""
  ))) {
    Trial.list[["p"]][[px]] <-
      ExtractTrialData(PartID = Subjidx[px], COND = "p")
  }
  else {
    Trial.list[["p"]][[px]] <- NA
  }
}
names(Trial.list[["p"]]) <- Subjidx

## Remove CLP116 pain data
Trial.list[["p"]][is.na(Trial.list[["p"]])] <- NULL

save(Trial.list,file = "Output/Trial_list.RData")

Trialdata <- rbind(data.table::rbindlist(Trial.list$np),
                 data.table::rbindlist(Trial.list$p))
write.csv(Trialdata,file = "Output/TrialData.csv",
          row.names = F)
}

## Load data
tmp = load("Output/Trial_list.RData")
Trialdata <- read.csv("Output/TrialData.csv")
Subjidx <- unique(Trialdata$PartID)
## Some extreme CTI and ITI values were found. See plots
# hist(Trialdata$CTI)
# hist(Trialdata$ITI)
# Participants 101,102,107 are clear outliers and appear to have some extra long CTIs

## Calculate summary variables and store in data frame
source('Functions/MethodsList.R')
Summdata <- MethodsList(Trialdata)
```

## 2.1. Participants
  A total of `r length(unique(Summdata$PartID))` participants were recruited for the study. They were recruited from *Insert here* and ranged in age from *X-Xyrs (X% Female)*. The study confirmed to ethics approved by *Ethics board of study*.

## 2.2. Procedure

### 2.2.X. Cross-modal Attention task

The Cross-modal Attention task requires participants to respond to either the position of a visual target or the pitch of an auditory target. Targets can appear simultaneously and so participants are presented with a cue to indicate the correct target in the upcoming trial. This version of the task consisted of three types of cues. Cues consisted of *Insert what cues looked like* presented on screen for *How long were cues presented?*. Cue *one* indicated the participant should respond to the position of the visual target. Cue *two* indicated that participants should respond to the pitch of the auditory target. These two cues occurred on `r round((1-(table(Trialdata$CueType)[[1]]/sum(table(Trialdata$CueType))))/2,1)*100`% of trials each. On the remaining `r round((table(Trialdata$CueType)[[1]]/sum(table(Trialdata$CueType))),1)*100`% of trials, participants received an ambiguous cue, which gave no information about the upcoming target. On these trials only one target was presented. Equal ratios of auditory and visual targets followed ambiguous cues (*I'm guessing this is true?*).

  Cues were displayed for 250ms and targets for 60ms [*Please confirm this is correct. Trigger codes did not specify exactly*]. The cue to target interval (CIT) jittered between `r round(min(Trialdata$CTI,na.rm=T),0)`-`r round(max(Trialdata$CTI,na.rm=T),0)` in steps of **XXX** (*Values for this change with participants. Some have maxes of ~800ms and min of ~700ms. Others (N = 3) have max ~1500 and min ~1400*). Each trial lasted approximately `r round(mean(Trialdata %>% group_by(PartID) %>% summarise(meanITI = mean(ITI,na.rm=T)) %>% .$meanITI),0)`, with a jitter of **XXX** (*Again, same three participants throw this estimate out*).

# 3. Results  
```{r Results Set-up, echo=FALSE}
## Create plots to observe possible outliers, effects, interactions etc

## Colour-blind friendly pallatte
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7","#000000")

## We will plot four main comparisons on RT:
# Modality (Auditory vs Visual targets)
# Preparation (Cued-targets vs Ambiguous Target)
# Interference/Distraction (Prescence vs Abscence of Targets)
# Pain (Pain vs No-Pain conditions) - which will be compared across all of the above.
if(!file.exists("Output/RT_Boxplots.pdf")){
  source("Functions/RT_Plots.R")
}
tmp =load(file = "Output/RT_Plots.RData")

#### Error Rates Calclations ####

# Create list of error rates splits of interest
N_Trials <- list()
N_Trials[["Condition"]] <- Trialdata %>% dplyr::group_by(PartID,Condition,Accuracy) %>%  dplyr::tally()

N_Trials[["CueType"]] <- Trialdata %>% dplyr::group_by(PartID,CueType,Accuracy) %>%  dplyr::tally()

N_Trials[["Distractor"]] <- Trialdata %>% dplyr::group_by(PartID,Distractor,Accuracy) %>%  dplyr::tally()

N_Trials[["Target"]] <- Trialdata %>% dplyr::group_by(PartID,Target,Accuracy) %>% dplyr::tally()

source('Functions/ErrRates.R')

Errors_list <- list()
for (i in seq_along(names(N_Trials))) {
  Errors_list[[names(N_Trials)[[i]]]] <- ErrRates(
    list = N_Trials,
    sublist = names(N_Trials)[[i]],
    sublist_levels = unique(N_Trials[[names(N_Trials)[[i]]]][[names(N_Trials)[[i]]]]),
    subj = Subjidx
  )
}

## Build Errors data.frame ##
Errorsdata <-
  data.frame(lapply(names(Errors_list), function(x)
    data.frame(Errors_list[[x]][["Errors"]])))
# Turns the length = 0 lists into NA and creates data.frame
for (i in names(Errorsdata)){
      Errorsdata[[i]] <- unlist(ifelse(sapply(Errorsdata[[i]], length) == 0, NA, Errorsdata[[i]]))
}
names(Errorsdata) <- c("NoPain","Pain",
                       "AmbiguousCue","AuditoryCue","VisualCue",
                       "DistractorAbsent","DistractorPresent",
                       "AuditoryTarget","VisualTarget")
# Build Misses data frame #
Missdata   <-
  data.frame(lapply(names(Errors_list), function(x)
    data.frame(Errors_list[[x]][["Ommissions"]])))

# Turns the length = 0 lists into NA and creates data.frame
for (i in names(Missdata)){
      Missdata[[i]] <- unlist(ifelse(sapply(Missdata[[i]], length) == 0, NA, Missdata[[i]]))
}
names(Missdata) <- c("NoPain","Pain",
                       "AmbiguousCue","AuditoryCue","VisualCue",
                       "DistractorAbsent","DistractorPresent",
                       "AuditoryTarget","VisualTarget")
# Clean as we go
rm(Errors_list)

## Create SPSS/JASP ready dataframe
# RT column with one column for each interaction of variables
SPSSdata <-
  reshape2::dcast(
    data = Trialdata %>% dplyr::filter(Accuracy != "Miss"),
    formula = PartID ~ Condition + CueType + Target + Distractor + Accuracy,
    fun.aggregate = mean,
    value.var = "RT"
  )
# Write to file
write.csv(SPSSdata, file = "Output/SPSSdata.csv",
          row.names = F)

# Error rates
# Write to file
SPSSdata <-
  reshape2::dcast(
    data = Errorsdata,
    formula = PartID ~ Condition + CueType + Target + Distractor,
    fun.aggregate = mean,
    value.var = "ErrorRates"
  )
write.csv(SPSSdata, file = "Output/Error_SPSSdata.csv",
          row.names = F)

write.csv(Errorsdata, file = "Output/Errors_data.csv",
          row.names = F)
# Ommissions rates
# Write to file
SPSSdata <-
  reshape2::dcast(
    data = Errorsdata,
    formula = PartID ~ Condition + CueType + Target + Distractor,
    fun.aggregate = mean,
    value.var = "MissRates"
  )
write.csv(SPSSdata, file = "Output/Miss_SPSSdata.csv",
          row.names = F)

write.csv(Missdata, file = "Output/Miss_data.csv",
          row.names = F)
```
## 3.1. Behavioural Results
```{r Table 1, echo=FALSE}
T1mean <- list()
# Mean RT
T1mean[["All"]] <-
  aggregate(RT ~ PartID + Condition + CueType + Target + Distractor + Accuracy,
            data = Trialdata,
            FUN = mean)
T1mean[["Modality"]] <- aggregate(RT ~ PartID + Target,
            data = Trialdata,
            FUN = mean)
T1mean[["Preparation"]] <- aggregate(RT ~ PartID + CueType,
            data = Trialdata,
            FUN = mean)
T1mean[["PrepTarget"]] <- aggregate(RT ~ PartID + CueType + Target,
                                 data = Trialdata,
                                 FUN = mean)
T1mean[["Distraction"]] <- aggregate(RT ~ PartID + Distractor,
            data = Trialdata,
            FUN = mean)
T1mean[["DistractionTarget"]] <-
  aggregate(RT ~ PartID + Distractor + Target,
            data = Trialdata,
            FUN = mean)
T1mean[["Condition"]] <- aggregate(RT ~ PartID + Condition,
            data = Trialdata,
            FUN = mean)
T1mean[["ConditionModality"]] <- aggregate(RT ~ PartID + Condition + Target,
            data = Trialdata,
            FUN = mean)
T1mean[["ConditionPreparation"]] <- aggregate(RT ~ PartID + Condition + CueType,
            data = Trialdata,
            FUN = mean)
T1mean[["ConditionDistraction"]] <- aggregate(RT ~ PartID + Condition + Distractor,
            data = Trialdata,
            FUN = mean)

# Number of Trials for Error calcs
NTrials <-
  aggregate(TrialNum ~ PartID + Condition + CueType + Target + Distractor + Accuracy,
            data = Trialdata,
            FUN = length)
names(NTrials)[length(NTrials)] <- "NTrials"
# Create grouping variable to help calc percentages
NTrials$levels <- interaction(NTrials$PartID,NTrials$Condition,NTrials$CueType,NTrials$Target,NTrials$Distractor,sep = ".")

ErrorRates <- list()
for (i in unique(NTrials$levels)) {
  dummy <- ((NTrials$NTrials[NTrials$levels == i &
                            NTrials$Accuracy == "Error"] / sum(NTrials$NTrials[NTrials$levels == i])) * 100)

  ErrorRates[["ErrorRates"]][[i]] <-
    unlist(ifelse(length(dummy) == 0, NA, dummy))

  dummy2 <- (NTrials$NTrials[NTrials$levels == i &
                            NTrials$Accuracy == "Miss"] / sum(NTrials$NTrials[NTrials$levels == i]) * 100)

  ErrorRates[["MissRates"]][[i]] <-
    unlist(ifelse(length(dummy2) == 0, NA, dummy2))
}
rm(dummy,dummy2)

Errorsdata <- data.frame(ErrorRates)
Errorsdata$levels <- rownames(Errorsdata)
foo <- do.call(rbind,strsplit(Errorsdata$levels,split = "[.]"))
colnames(foo) <- names(T1mean$All)[1:ncol(foo)]
Errorsdata <- cbind(foo,Errorsdata) %>% select(-levels)

T1err <- list()
T1err[["Modality"]] <- 
  aggregate(ErrorRates ~ PartID + Target,
            data = Errorsdata,
            FUN = mean)
T1err[["Preparation"]] <-
  aggregate(ErrorRates ~ PartID + CueType, 
            data = Errorsdata, 
            FUN = mean)
T1err[["PrepTarget"]] <- aggregate(ErrorRates ~ PartID + CueType + Target,
                                 data = Errorsdata,
                                 FUN = mean)
T1err[["Distraction"]] <-
  aggregate(ErrorRates ~ PartID + Distractor,
            data = Errorsdata,
            FUN = mean)
T1err[["DistractionTarget"]] <-
  aggregate(ErrorRates ~ PartID + Distractor + Target,
            data = Errorsdata,
            FUN = mean)
T1err[["Condition"]] <- 
  aggregate(ErrorRates ~ PartID + Condition,
            data = Errorsdata,
            FUN = mean)

T1omm <- list()
T1omm[["Modality"]] <- 
  aggregate(MissRates ~ PartID + Target,
            data = Errorsdata,
            FUN = mean)
T1omm[["Preparation"]] <-
  aggregate(MissRates ~ PartID + CueType, 
            data = Errorsdata, 
            FUN = mean)
T1omm[["Distraction"]] <-
  aggregate(MissRates ~ PartID + Distractor,
            data = Errorsdata,
            FUN = mean)
T1omm[["DistractionTarget"]] <-
  aggregate(MissRates ~ PartID + Distractor + Target,
            data = Errorsdata,
            FUN = mean)
T1omm[["PrepTarget"]] <- aggregate(MissRates ~ PartID + CueType + Target,
                                 data = Errorsdata,
                                 FUN = mean)
T1omm[["Condition"]] <- 
  aggregate(MissRates ~ PartID + Condition,
            data = Errorsdata,
            FUN = mean)
```

### 3.1.1. Modality Effects
Visual targets (`r round(mean(T1mean$Modality$RT[T1mean$Modality$Target=="Visual"]),2)` ± `r round(stderr(T1mean$Modality$RT[T1mean$Modality$Target=="Visual"]),2)`) were identified faster than auditory targets (`r round(mean(T1mean$Modality$RT[T1mean$Modality$Target=="Auditory"]),2)` ± `r round(stderr(T1mean$Modality$RT[T1mean$Modality$Target=="Auditory"]),2)`). The percentage of errer trials was higher for auditory targets compared to visual targets. Visual targets were incorrectly responded to on `r round(mean(T1err$Modality$ErrorRates[T1err$Modality$Target=="Visual"]),2)` ± `r round(stderr(T1err$Modality$ErrorRates[T1err$Modality$Target=="Visual"]),2)`% trials, while auditory targets had an error rate of `r round(mean(T1err$Modality$ErrorRates[T1err$Modality$Target=="Auditory"]),2)` ± `r round(stderr(T1err$Modality$ErrorRates[T1err$Modality$Target=="Auditory"]),2)`%. Given the low error rates, RTs to error trials were not examined here (but see Figure 1). Omissions across each target type was low (Visual = `r round(mean(T1omm$Modality$MissRates[T1err$Modality$Target=="Visual"],na.rm=T),2)`%, Auditory = `r round(mean(T1omm$Modality$MissRates[T1err$Modality$Target=="Visual"],na.rm=T),2)`%).

```{r Figureone, echo=FALSE, fig.cap = 'Violin plot of RT to visual and auditory targets. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean', message=FALSE}
Plots$Modality$Accuracy
```

### 3.1.2. Preparatory Effects
To examine the effect of preparation, reaction times of trials with informative cues were compared to trials with ambiguous cues. Correct trial RTs for auditory targets decreased from `r round(mean(T1mean$PrepTarget$RT[T1mean$PrepTarget$CueType=="Ambiguous" & T1mean$PrepTarget$Target=="Auditory"]),2)` ± `r round(stderr(T1mean$PrepTarget$RT[T1mean$PrepTarget$CueType=="Ambiguous" & T1mean$PrepTarget$Target=="Auditory"]),2)`ms for ambiguous cues to `r round(mean(T1mean$PrepTarget$RT[T1mean$PrepTarget$CueType=="Auditory" & T1mean$PrepTarget$Target=="Auditory"]),2)` ± `r round(stderr(T1mean$PrepTarget$RT[T1mean$PrepTarget$CueType=="Auditory" & T1mean$PrepTarget$Target=="Auditory"]),2)`ms for informative cues. For visual targets the average RT decreased from `r round(mean(T1mean$PrepTarget$RT[T1mean$PrepTarget$CueType=="Ambiguous" & T1mean$PrepTarget$Target=="Visual"]),2)` ± `r round(stderr(T1mean$PrepTarget$RT[T1mean$PrepTarget$CueType=="Ambiguous" & T1mean$PrepTarget$Target=="Visual"]),2)` ms for ambiguous cues to `r round(mean(T1mean$PrepTarget$RT[T1mean$PrepTarget$CueType=="Visual" & T1mean$PrepTarget$Target=="Visual"]),2)` ± `r round(stderr(T1mean$PrepTarget$RT[T1mean$PrepTarget$CueType=="Visual" & T1mean$PrepTarget$Target=="Visual"]),2)` ms for informative cues. The faster identification of trials with an informative cue suggest that top-down processes facilitated target processing.

```{r Figuretwo, echo=FALSE, message=FALSE,fig.cap= 'Violin plot of RT to ambiguous and informatively cued targets, split by correct and erronous responses and target type. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean.'}
gridExtra::grid.arrange(Plots$Preparation$Accuracy,
Plots$Preparation$Modality)
```

Cues had the opposite influence on task accuracy. Auditory targets were incorrectly responded to in `r round(mean(T1err$PrepTarget$ErrorRates[T1err$PrepTarget$CueType=="Ambiguous" & T1err$PrepTarget$Target=="Auditory"]),2)` ± `r round(stderr(T1err$PrepTarget$ErrorRates[T1err$PrepTarget$CueType=="Ambiguous" & T1err$PrepTarget$Target=="Auditory"]),2)`% of trials with an uninformative cue and in `r round(mean(T1err$PrepTarget$ErrorRates[T1err$PrepTarget$CueType=="Auditory" & T1err$PrepTarget$Target=="Auditory"]),2)` ± `r round(stderr(T1err$PrepTarget$ErrorRates[T1err$PrepTarget$CueType=="Auditory" & T1err$PrepTarget$Target=="Auditory"]),2)`% with an informative cue. However, visual targets showed little difference in error rates between trials with ambiguous cues (`r round(mean(T1err$PrepTarget$ErrorRates[T1err$PrepTarget$CueType=="Ambiguous" & T1err$PrepTarget$Target=="Visual"]),2)` ± `r round(stderr(T1err$PrepTarget$ErrorRates[T1err$PrepTarget$CueType=="Ambiguous" & T1err$PrepTarget$Target=="Visual"]),2)`%) and trials with informative cues (`r round(mean(T1err$PrepTarget$ErrorRates[T1err$PrepTarget$CueType=="Visual" & T1err$PrepTarget$Target=="Visual"]),2)` ± `r round(stderr(T1err$PrepTarget$ErrorRates[T1err$PrepTarget$CueType=="Visual" & T1err$PrepTarget$Target=="Visual"]),2)`%). As noted above, there was a probable ceiling effect on performance. However, omission rates showed some considerable differences between targets based upon whether they were cued or not. Omissions occurred on `r round(mean(T1omm$PrepTarget$MissRates[T1omm$PrepTarget$CueType == "Ambiguous" & T1omm$PrepTarget$Target == "Auditory"]), 2)` ± `r round(stderr(T1omm$PrepTarget$MissRates[T1omm$PrepTarget$CueType == "Ambiguous" & T1omm$PrepTarget$Target == "Auditory"]), 2)`% of auditory trials with an ambiguous cue. In comparison, informatively cued auditory trials contained `r round(mean(T1omm$PrepTarget$MissRates[T1omm$PrepTarget$CueType == "Auditory" & T1omm$PrepTarget$Target == "Auditory"]), 2)` ± `r round(stderr(T1omm$PrepTarget$MissRates[T1omm$PrepTarget$CueType == "Auditory" & T1omm$PrepTarget$Target == "Auditory"]), 2)`% omissions. A similar effect is seen with visual targets. Ambiguously cued visual targets contained `r round(mean(T1omm$PrepTarget$MissRates[T1omm$PrepTarget$CueType == "Ambiguous" & T1omm$PrepTarget$Target == "Visual"]), 2)` ± `r round(stderr(T1omm$PrepTarget$MissRates[T1omm$PrepTarget$CueType == "Ambiguous" & T1omm$PrepTarget$Target == "Visual"]), 2)`% of omissions, while informatively cued trials contained `r round(mean(T1omm$PrepTarget$MissRates[T1omm$PrepTarget$CueType == "Ambiguous" & T1omm$PrepTarget$Target == "Visual"]), 2)` ± `r round(stderr(T1omm$PrepTarget$MissRates[T1omm$PrepTarget$CueType == "Ambiguous" & T1omm$PrepTarget$Target == "Visual"]), 2)`% omission trials.

### 3.1.3. Distraction Effects
To test whether participants were disturbed by the presentation of distract ors in a different modality, RTs from trials containing distractors were compared to RTs from the distractor absent trials. Informatively cued Auditory trials without distractors had mean RT of `r round(mean(T1mean$DistractionTarget$RT[T1mean$DistractionTarget$Distractor == "Absent" & T1mean$DistractionTarget$Target == "Auditory"]), 2)` ± `r round(stderr(T1mean$DistractionTarget$RT[T1mean$DistractionTarget$Distractor == "Absent" & T1mean$DistractionTarget$Target == "Auditory"]), 2)`ms, while Auditory trials with distraction had mean RT of `r round(mean(T1mean$DistractionTarget$RT[T1mean$DistractionTarget$Distractor == "Present" & T1mean$DistractionTarget$Target == "Auditory"]), 2)` ± `r round(stderr(T1mean$DistractionTarget$RT[T1mean$DistractionTarget$Distractor == "Present" & T1mean$DistractionTarget$Target == "Auditory"]), 2)`ms. Similarly, Visual targets had slower RT when distractions were present (`r round(mean(T1mean$DistractionTarget$RT[T1mean$DistractionTarget$Distractor == "Present" & T1mean$DistractionTarget$Target == "Visual"]), 2)` ± `r round(stderr(T1mean$DistractionTarget$RT[T1mean$DistractionTarget$Distractor == "Present" & T1mean$DistractionTarget$Target == "Visual"]), 2)`ms) compared to without (`r round(mean(T1mean$DistractionTarget$RT[T1mean$DistractionTarget$Distractor == "Absent" & T1mean$DistractionTarget$Target == "Visual"]), 2)` ± `r round(stderr(T1mean$DistractionTarget$RT[T1mean$DistractionTarget$Distractor == "Absent" & T1mean$DistractionTarget$Target == "Visual"]), 2)`ms). Presentation of a distractor in a different modality is detrimental for task performance and a mechanism for active inhibition of distractors could be beneficial during this task.

```{r Figurethree, echo=FALSE, message=FALSE, fig.cap= 'Violin plot of RT to targets with and without distraction, split by correct and erronous responses. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean.'}
gridExtra::grid.arrange(Plots$Distraction$Accuracy,
Plots$Distraction$Modality)
```

### 3.1.4. Pain Effects
The effect of pain on performance can be measured in a number of ways. Overall RT was relatively similar in the pain (`r round(mean(T1mean$Condition$RT[T1mean$Condition$Condition == "p"]), 2)` ± `r round(stderr(T1mean$Condition$RT[T1mean$Condition$Condition == "p"]), 2)`) vs no pain conditions (`r round(mean(T1mean$Condition$RT[T1mean$Condition$Condition == "np"]), 2)` ± `r round(stderr(T1mean$Condition$RT[T1mean$Condition$Condition == "np"]), 2)`). Likewise, overall error rates in the pain condition (`r round(mean(T1err$Condition$ErrorRates[T1err$Condition$Condition == "p"]), 2)` ± `r round(stderr(T1err$Condition$ErrorRates[T1err$Condition$Condition == "p"]), 2)`) were similar to the no pain condition (`r round(mean(T1err$Condition$ErrorRates[T1err$Condition$Condition == "np"]), 2)` ± `r round(stderr(T1err$Condition$ErrorRates[T1err$Condition$Condition == "np"]), 2)`). Omission rates were also found to be comparable across conditions (pain = `r round(mean(T1omm$Condition$MissRates[T1omm$Condition$Condition == "p"]), 2)` ± `r round(stderr(T1omm$Condition$MissRates[T1omm$Condition$Condition == "p"]), 2)`, no pain = `r round(mean(T1omm$Condition$MissRates[T1omm$Condition$Condition == "np"]), 2)` ± `r round(stderr(T1omm$Condition$MissRates[T1omm$Condition$Condition == "np"]), 2)`). Therefore an overall affect of condition on performance was not present. However, pain may influence specific effects of preparation and distraction.

```{r Figurefour, echo=FALSE, message=FALSE,fig.cap= 'Violin plot of RT with and without pain, split by correct and erronous responses. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean.'}
Plots$Condition$Accuracy
```

### 3.1.5. Pain Interactions
The RT benefit of visual targets was the same across pain (Auditory - Visual RT = `r round(mean(T1mean$ConditionModality$RT[T1mean$ConditionModality$Target=="Auditory"& T1mean$ConditionModality$Condition=="p"])-mean(T1mean$ConditionModality$RT[T1mean$ConditionModality$Target=="Visual" & T1mean$ConditionModality$Condition=="p"]),2)` ± `r round(stderr(T1mean$ConditionModality$RT[T1mean$ConditionModality$Target=="Auditory"& T1mean$ConditionModality$Condition=="p"])-stderr(T1mean$ConditionModality$RT[T1mean$ConditionModality$Target=="Visual" & T1mean$ConditionModality$Condition=="p"]),2)`) and no pain conditions (Auditory - Visual RT = `r round(mean(T1mean$ConditionModality$RT[T1mean$ConditionModality$Target=="Auditory"& T1mean$ConditionModality$Condition=="np"])-mean(T1mean$ConditionModality$RT[T1mean$ConditionModality$Target=="Visual" & T1mean$ConditionModality$Condition=="np"]),2)` ± `r round(stderr(T1mean$ConditionModality$RT[T1mean$ConditionModality$Target=="Auditory"& T1mean$ConditionModality$Condition=="np"])-stderr(T1mean$ConditionModality$RT[T1mean$ConditionModality$Target=="Visual" & T1mean$ConditionModality$Condition=="np"]),2)`).

```{r Figurefive, echo=FALSE, message=FALSE,fig.cap= 'Violin plot of RT with and without pain, split by Target. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean.'}
Plots$Condition$Modality
```

In the pain condition, there was only a small improvement in preparation costs. Ambiguous cues were `r round(mean(T1mean$ConditionPreparation$RT[T1mean$ConditionPreparation$CueType == "Ambiguous" & T1mean$ConditionPreparation$Condition == "p"]) - mean(T1mean$ConditionPreparation$RT[T1mean$ConditionPreparation$CueType != "Ambiguous" & T1mean$ConditionPreparation$Condition == "p"]),2)` ± `r round(stderr(T1mean$ConditionPreparation$RT[T1mean$ConditionPreparation$CueType == "Ambiguous" & T1mean$ConditionPreparation$Condition == "p"]) - stderr(T1mean$ConditionPreparation$RT[T1mean$ConditionPreparation$CueType != "Ambiguous" & T1mean$ConditionPreparation$Condition == "p"]),2)`ms slower compared to informatively cued trials in the pain condition. However, this difference was  `r round(mean(T1mean$ConditionPreparation$RT[T1mean$ConditionPreparation$CueType == "Ambiguous" & T1mean$ConditionPreparation$Condition == "np"]) - mean(T1mean$ConditionPreparation$RT[T1mean$ConditionPreparation$CueType != "Ambiguous" & T1mean$ConditionPreparation$Condition == "np"]),2)` ± `r round(stderr(T1mean$ConditionPreparation$RT[T1mean$ConditionPreparation$CueType == "Ambiguous" & T1mean$ConditionPreparation$Condition == "np"]) - stderr(T1mean$ConditionPreparation$RT[T1mean$ConditionPreparation$CueType != "Ambiguous" & T1mean$ConditionPreparation$Condition == "np"]),2)`ms in the no pain condition.

```{r Figuresix, echo=FALSE, fig.cap='Violin plot of RT with and without pain, split by cue type. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean.', message=FALSE}
Plots$Condition$Preparation
```

Distraction effects showed little differences between the pain condition (`r round(mean(T1mean$ConditionDistraction$RT[T1mean$ConditionDistraction$Distractor == "Present" & T1mean$ConditionDistraction$Condition == "p"]) - mean(T1mean$ConditionDistraction$RT[T1mean$ConditionDistraction$Distractor == "Absent" & T1mean$ConditionDistraction$Condition == "p"]),2)` ± `r round(mean(T1mean$ConditionDistraction$RT[T1mean$ConditionDistraction$Distractor == "Present" & T1mean$ConditionDistraction$Condition == "p"]) - stderr(T1mean$ConditionDistraction$RT[T1mean$ConditionDistraction$Distractor == "Absent" & T1mean$ConditionDistraction$Condition == "p"]),2)`) and no pain conditions (`r round(mean(T1mean$ConditionDistraction$RT[T1mean$ConditionDistraction$Distractor == "Present" & T1mean$ConditionDistraction$Condition == "np"]) - stderr(T1mean$ConditionDistraction$RT[T1mean$ConditionDistraction$Distractor == "Absent" & T1mean$ConditionDistraction$Condition == "np"]),2)` ± `r round(mean(T1mean$ConditionDistraction$RT[T1mean$ConditionDistraction$Distractor == "Present" & T1mean$ConditionDistraction$Condition == "np"]) - stderr(T1mean$ConditionDistraction$RT[T1mean$ConditionDistraction$Distractor == "Absent" & T1mean$ConditionDistraction$Condition == "np"]),2)`).

```{r Figureseven, echo=FALSE, message=FALSE,fig.cap= 'Violin plot of RT with and without pain, split by prescence of distractor. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean.'}
Plots$Condition$Distraction
```

## 3.1. Behavioural Results Models
```{r RT Tests, eval=FALSE, include=FALSE}
## Just do this in JASP ##

# ## Linear Models take longer than straight ANOVAs?
# RTBayeslm_all <-
#   BayesFactor::anovaBF(
#     RT ~ Target * CueType * Condition + PartID,
#     data = Trialdata[!is.na(Trialdata$RT),],
#     whichRandom = "PartID",
#     progress = T,
#     iterations = 10
# )
# 
# RTBayeslm_NullComparison <- head(RTBayeslm_all)/max(RTBayeslm_all)
# ## See differences between most supported model
# plot(RTBayeslm_NullComparison)
```

```{r PAF Anal}
## Subjects
EEGSubj <- as.character(Subjidx)
EEGSubj[length(EEGSubj)+1] <- "CLP130"
EEGSubj <- EEGSubj[c(1:29,32,30,31)]

## Electrodes
electrodes <- read.csv("EEG_Output/ElectrodeLabels.csv")

## Analysis of Alpha EEG Data ##
Alpha <- rmatio::read.mat("EEG_Output/ImpAlphaPower.mat")
Alpha[["np"]] <- data.frame(Alpha$AlphaPower[,1,])
names(Alpha[["np"]]) <- electrodes[!electrodes=="Cz"]
Alpha[["np"]]$PartID <- EEGSubj
Alpha[["np"]]$Condition <- "np"
Alpha[["np"]][Alpha[["np"]]==0] <- NA
Alpha[["p"]] <- data.frame(Alpha$AlphaPower[,2,])
names(Alpha[["p"]]) <- electrodes[!electrodes=="Cz"]
Alpha[["p"]]$PartID <- EEGSubj
Alpha[["p"]]$Condition <- "p"
Alpha[["p"]][Alpha[["p"]]==0] <- NA

AlphaPower <- rbind(Alpha[["np"]],Alpha[["p"]])
AlphaPower$Variable <- "AlphaPower"

## Analysis of Peak Alpha Frequency EEG Data ##
PAF <- rmatio::read.mat("EEG_Output/ImpPeakFrequency.mat")
PAF[["np"]] <- data.frame(PAF$PeakFrequency[,1,])
names(PAF[["np"]]) <- electrodes[!electrodes=="Cz"]
PAF[["np"]]$PartID <- EEGSubj
PAF[["np"]]$Condition <- "np"
PAF[["np"]][PAF[["np"]]==0] <- NA
PAF[["p"]] <- data.frame(PAF$PeakFrequency[,2,])
names(PAF[["p"]]) <- electrodes[!electrodes=="Cz"]
PAF[["p"]]$PartID <- EEGSubj
PAF[["p"]]$Condition <- "p"
PAF[["p"]][PAF[["p"]]==0] <- NA

PAF <- rbind(PAF[["np"]],PAF[["p"]])
PAF$Variable <- "PAF"

# ## Analysis of Spectra EEG Data ##
# PAF <- rmatio::read.mat("EEG_Output/ImpPeakFrequency.mat")
# PAF[["np"]] <- data.frame(PAF$PeakFrequency[,1,])
# names(PAF[["np"]]) <- electrodes[!electrodes=="Cz"]
# PAF[["np"]]$PartID <- EEGSubj
# PAF[["np"]]$Condition <- "np"
# PAF[["np"]][PAF[["np"]]==0] <- NA
# PAF[["p"]] <- data.frame(PAF$PeakFrequency[,2,])
# names(PAF[["p"]]) <- electrodes[!electrodes=="Cz"]
# PAF[["p"]]$PartID <- EEGSubj
# PAF[["p"]]$Condition <- "p"
# PAF[["p"]][PAF[["p"]]==0] <- NA
# 
# PAF <- rbind(PAF[["np"]],PAF[["p"]])
# PAF$Variable <- "PAF"

# Combine and make a long dataset
EEG_Measures <- rbind(AlphaPower,PAF)
write.csv(EEG_Measures,file = "Output/EEG_Measures.csv",row.names = F)
# Make Long for plotting
EEG_Plot <- reshape2::melt(EEG_Measures,
                           id.vars = c("PartID","Condition","Variable"),
                           value.name = "Amplitude",
                           variable.name = "Site")
write.csv(EEG_Plot,file = "Output/EEG_Measureslong.csv",row.names = F)

```

```{r Plot EEG Measures}
SOI <- c("Fz","FCz","Cz","C3","C4","CPz","Pz")
  EEG_Plot %>% 
  dplyr::filter(Variable=="AlphaPower",Site %in% SOI) %>% 
  ggplot(aes(y = Amplitude,
             colour = Condition,
             x = Site)) +
    geom_jitter()+
  geom_violin(alpha = 0,
              scale = "width",
              adjust = .5,
              draw_quantiles = c(.5)) +
  # scale_fill_manual(name = "Condition",
  #                   labels = c("No Pain", "Pain"),
  #                   values = cbbPalette) +
      scale_colour_manual(name = "Condition",
                    labels = c("No Pain", "Pain"),
                    values = cbbPalette) +
  ylab("Hz") +
  theme_classic()
  ggsave("Output/AlphaPlot.tiff")
  # geom_errorbar(data = wse[["TargetAccuracy"]],
  #               aes(ymin = RT - se,
  #                   ymax = RT + se),
  #               lwd = .3,
  #               width = .5,
  #               position = position_dodge(.9))

```

### 2020-05-13 ManuscriptMarkdown.tex
Establish repo for analysis

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  ,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Cross frequency coupling of attentional EEG task under pain},
  pdfborder={0 0 0},
  breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-2}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Cross Pain}
\author{Patrick Skippen\textsuperscript{1}, David Seminowicz\textsuperscript{1}, Ali Mazaheri\textsuperscript{2}, Samantha Mallard\textsuperscript{1}, \& Siobhan Schabrun\textsuperscript{1}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Neuroscience Research Australia, Randwick Australia\\\textsuperscript{2} Where-ever Ali is, Country}
\authornote{

Author's  contributions: DS and AM conceptualised the research plan and raitonale. PS took the lead role in manuscript preparation, formulated the analysis plan, and undertook majority of the data analysis. SS xyz.
The data and code used to create this manuscript can be found at https://osf.io/XXXX/
This is version 1: 02/2020

Correspondence concerning this article should be addressed to Patrick Skippen, Neuroscience Research Australia, Barker St, Randwick, Australia. E-mail: p.skippen@neura.edu.au}
\note{\textbackslash{}clearpage}
\keywords{}
\usepackage{csquotes}
\usepackage{float}
\usepackage{caption}
\floatplacement{figure}{H}
\raggedbottom
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\ifnum 0\ifxetex 1\fi=0 % if pdftex or luatex
  \usepackage[shorthands=off,main=english]{babel}
\else % if xetex
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi

\title{Cross frequency coupling of attentional EEG task under pain}

\date{}

\abstract{
blah blah.
}

\begin{document}
\maketitle

\setlength{\abovedisplayskip}{-20pt}
\setlength{\belowdisplayskip}{3pt}
\setlength{\abovedisplayshortskip}{-30pt}
\setlength{\belowdisplayshortskip}{3pt}

\hypertarget{introduction}{%
\section{1. Introduction}\label{introduction}}

\hypertarget{methods}{%
\section{2. Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{2.1. Participants}\label{participants}}

A total of 31 participants were recruited for the study. They were recruited from \emph{Insert here} and ranged in age from \emph{X-Xyrs (X\% Female)}. The study confirmed to ethics approved by \emph{Ethics board of study}.

\hypertarget{procedure}{%
\subsection{2.2. Procedure}\label{procedure}}

\hypertarget{x.-cross-modal-attention-task}{%
\subsubsection{2.2.X. Cross-modal Attention task}\label{x.-cross-modal-attention-task}}

The Cross-modal Attention task requires participants to respond to either the position of a visual target or the pitch of an auditory target. Targets can appear simultaneously and so participants are presented with a cue to indicate the correct target in the upcoming trial. This version of the task consisted of three types of cues. Cues consisted of \emph{Insert what cues looked like} presented on screen for \emph{How long were cues presented?}. Cue \emph{one} indicated the participant should respond to the position of the visual target. Cue \emph{two} indicated that participants should respond to the pitch of the auditory target. These two cues occured on 40\% of trials each. On the remaining 20\% of trials, participants recieved an ambiguous cue, which gave no information about the upcoming target. On these trials only one target was presented. Equal ratios of auditory and visual targets followed ambiguous cues (\emph{I'm guessing this is true?}).

Cues were displayed for 250ms and targets for 60ms {[}\emph{Please confirm this is correct. Trigger codes did not specify exactly}{]}. The cue to target interval (CIT) jittered between 684-1644 in steps of \textbf{XXX} (\emph{Values for this change with participants. Some have maxs of \textasciitilde{}800ms and min of \textasciitilde{}700ms. Others (N = 3) have max \textasciitilde{}1500 and min \textasciitilde{}1400}). Each trial lasted approximately 2613, with a jitter of \textbf{XXX} (\emph{Again, same three participants throw this estimate out}).

\hypertarget{results}{%
\section{3. Results}\label{results}}

\hypertarget{behavioural-results}{%
\subsection{3.1. Behavioural Results}\label{behavioural-results}}

\hypertarget{modality-effects}{%
\subsubsection{3.1.1. Modality Effects}\label{modality-effects}}

Visual targets (341.63 +/- 16.43) were identified faster than auditory targets (444.97 +/- 22.50). The percentage of errer trials was higher for auditory targets compared to visual targets. Visual targets were incorrectly responded to on 3.36 +/- 0.26\% trials, while auditory targets had an error rate of 11.17 +/- 1.37\%. Given the low error rates, RTs to error trials were not examined here (but see Figure 1). Omissions across each target type was low (Visual = 5.18\%, Auditory = 5.18\%).

\begin{figure}
\centering
\includegraphics{ManuscriptMarkdown_files/figure-latex/Figureone-1.pdf}
\caption{\label{fig:Figureone}Violin plot of RT to visual and auditory targets. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean}
\end{figure}

\hypertarget{preparatory-effects}{%
\subsubsection{3.1.2. Preparatory Effects}\label{preparatory-effects}}

To examine the effect of preparation, reaction times of trials with informative cues were compared to trials with ambiguous cues. Correct trial RTs for auditory targets decreased from 468.20 +/- 24.66ms for ambiguous cues to 439.11 +/- 22.01ms for informative cues. For visual targets the average RT decreased from 349.56 +/- 17.04 ms for ambiguous cues to 339.63 +/- 16.39 ms for informative cues. The faster identification of trials with an informative cue suggest that top-down processes facilitated target processing.

\begin{figure}
\centering
\includegraphics{ManuscriptMarkdown_files/figure-latex/Figuretwo-1.pdf}
\caption{\label{fig:Figuretwo}Violin plot of RT to ambiguous and informatively cued targets, split by correct and erronous responses. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean.}
\end{figure}

Cues had the opposite influence on task accuracy. Auditory targets were incorrectly responded to in 9.52 +/- 1.40\% of trials with an uninformative cue and in 11.94 +/- 1.53\% with an informative cue. However, visual targets showed little difference in error rates between trials with ambiguous cues (3.65 +/- 0.29\%) and trials with informative cues (3.40 +/- 0.32\%). As noted above, there was a probable ceiling effect on performance. However, omission rates showed some considerable differences between targets based upon whether they were cued or not. Omissions occured on 10.18 +/- 1.63\% of auditory trials with an ambiguos cue. In comparison, informatively cued auditory trials contained 7.52 +/- 1.07\% omissions. A similar effect is seen with visual targets. Ambiguously cued visual targets contained 8.05 +/- 2.22\% of omissions, while informatively cued trials contained 8.05 +/- 2.22\% omission trials.

\hypertarget{distraction-effects}{%
\subsubsection{3.1.3. Distraction Effects}\label{distraction-effects}}

To test whether participants were disturbed by the presentation of distractors in a different modality, RTs from trials containing distractors were compared to RTs from the distractor absent trials. Informatively cued Auditory trials without distractors had mean RT of 435.36 +/- 23.96ms, while Auditory trials with distraction had mean RT of 459.99 +/- 20.68ms. Similary, Visual targets had slower RT when distractions were present (362.49 +/- 16.36ms) compared to without (327.95 +/- 16.79ms). Presentation of a distractor in a different modality is detrimental for task performance and a mechanism for active inhibition of distractors could be beneficial during this task.

\begin{figure}
\centering
\includegraphics{ManuscriptMarkdown_files/figure-latex/Figurethree-1.pdf}
\caption{\label{fig:Figurethree}Violin plot of RT to targets with and without distraction, split by correct and erronous responses. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean.}
\end{figure}

\hypertarget{pain-effects}{%
\subsubsection{3.1.4. Pain Effects}\label{pain-effects}}

The effect of pain on performance can be measured in a number of ways. Overall RT was relatively similar in the pain (388.79 +/- 20.20) vs no pain conditions (393.74 +/- 18.74). Likewise, overall error rates in the pain condition (8.48 +/- 1.08) were similar to the no pain condition (8.24 +/- 0.82). Omission rates were also found to be comparable across conditions (pain = 6.11 +/- 0.81, no pain = 7.13 +/- 0.97). Therefore an overall affect of condtion on performance was not present. However, pain may influence specific effects of preparation and distraction.

\begin{figure}
\centering
\includegraphics{ManuscriptMarkdown_files/figure-latex/Figurefour-1.pdf}
\caption{\label{fig:Figurefour}Violin plot of RT with and without pain, split by correct and erronous responses. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean.}
\end{figure}

\hypertarget{pain-interactions}{%
\subsubsection{3.1.5. Pain Interactions}\label{pain-interactions}}

The RT benefit of visual targets was the same across pain (Auditory - Visual RT = 106.84 +/- 6.07) and no pain conditions (Auditory - Visual RT = 100.86 +/- 6.03).

\begin{verbatim}
NULL
\end{verbatim}

In the pain condition, there was only a small improvement in preparation costs. Ambiguous cues were 17.45 +/- 6.15ms slower compared to informatively cued trials in the pain condition. However, this difference was 19.29 +/- 5.16ms in the no pain condition.

\begin{figure}
\centering
\includegraphics{ManuscriptMarkdown_files/figure-latex/Figuresix-1.pdf}
\caption{\label{fig:Figuresix}Violin plot of RT with and without pain, split by cue type. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean.}
\end{figure}

Distraction effects showed little differences between the pain condition (28.38 +/- 384.88) and no pain conditions (392.06 +/- 392.06).

\begin{figure}
\centering
\includegraphics{ManuscriptMarkdown_files/figure-latex/Figureseven-1.pdf}
\caption{\label{fig:Figureseven}Violin plot of RT with and without pain, split by prescence of distractor. Median RT is presented as a horizontal line in each violin, with error bars displaying the standard error of the mean.}
\end{figure}

\end{document}

### 2020-05-13 Functions/ErrRates.R

@@ -1,0 +1,33 @@
+ErrRates <- function(list, sublist, sublist_levels,subj) {
+  ErrorRates <- list()
+  OmmRates   <- list()
+  
+  for (i in seq_along(subj)) {
+    ## Create a dummy variable to store participant level data
+    subjdummy <- list[[sublist]][list[[sublist]]$PartID == subj[i], ]
+    ## Loop through participants and apply a percentage to each level of the list
+    OmmRates[[i]] <-
+      lapply(sublist_levels, function(x)
+        (subjdummy$n[subjdummy[[sublist]] == x &
+                       subjdummy$Accuracy == "Miss"] / sum(subjdummy$n[subjdummy[[sublist]] == x])) * 100)
+    names(OmmRates[[i]]) <- sublist_levels
+  
+    ## Do the same for errors
+    ErrorRates[[i]] <-
+      lapply(sublist_levels, function(x)
+        (subjdummy$n[subjdummy[[sublist]] == x &
+                       subjdummy$Accuracy == "Error"] / sum(subjdummy$n[subjdummy[[sublist]] == x])) * 100)
+    names(ErrorRates[[i]]) <- sublist_levels
+    
+  }
+  names(OmmRates) <- subj
+  names(ErrorRates) <- subj
+  ## Transform into data frames
+  
+  
+  OmmRates.data <- data.frame(do.call(rbind,OmmRates))
+  ErrorRates.data <- data.frame(do.call(rbind,ErrorRates))
+  
+  return(list(Errors = ErrorRates.data,
+              Ommissions = OmmRates.data))
+}

### 2020-05-13 Functions/ExtractRT_MATLAB.R

@@ -1,0 +1,316 @@
+ExtractTrialData <- function(PartID,COND){
+
+## Code to extract RT values from MATLAB event structures
+
+require(rmatio)
+require(dplyr)
+
+## Import Data
+mat <-
+  rmatio::read.mat(paste("../Data/",PartID,"/Behavior/",
+                         paste(PartID,COND,sep = "_"),
+                         "_EventCodes.mat",sep = ""))
+
+EventData <- data.frame(Lat = unlist(mat$EventCodes$latency),
+                        Trig = mat$EventCodes$type)
+
+## Triggers of Interest; Stimulus codes, Target Codes, Response Codes
+TOI <- list()
+TOI[['Stim']] <- c("S  1","S  2","S  3")
+TOI[['Target']] <- c("S101","S102","S103",
+                     "S110","S112","S113",
+                     "S121","S120","S123",
+                     "S131","S132","S130")
+TOI[["Resp"]] <- c("S201","S202","S203") # The first participants have these codes
+                   # "S 73","S 74","S 75") # The px CLP130 had these codes
+TOI[["TrialEnd"]] <- "S 50"
+
+## Trigger codes are organised as follows:
+# Cue: 1 = Visual, 2 = Auditory, 3 = Ambiguous
+# Target: 1VA where V = Visual target, A = Auditory target
+# E.g., 123 = Visual Target indicating middle resp; Auditory Target indicating Right response
+# e.g., 101 = No Visual target; Auditory Target indicating Left response
+# Repsonse: 1 = Left, 2 = Middle, 3 = Right.
+
+
+## RT on trial one:
+CueCode  <- which(EventData$Trig %in% TOI[["Stim"]]) # pos. of Cue Trig Codes
+TargCode <- which(EventData$Trig %in% TOI[["Target"]]) # pos. of Target Trig Codes
+RespCode <- which(EventData$Trig %in% TOI[["Resp"]]) # pos. of Response Trig Codes
+ErrCheck <- which((TargCode+2) %in% RespCode)
+
+# Misses (omissions) are not recorded.
+# Instead the response code is positioned after the end of the trial
+# Likewise, some double presses are coded.
+
+## Create list with each trial as seperate dataframe
+TrialList <- list()
[…]

### 2020-05-13 Functions/ExtractRT_MATLAB_1.R

@@ -1,0 +1,308 @@
+ExtractTrialData <- function(PartID,COND){
+
+## Code to extract RT values from MATLAB event structures
+
+require(rmatio)
+require(dplyr)
+
+## Import Data
+mat <-
+  rmatio::read.mat(paste("../Data/",PartID,"/Behavior/",
+                         paste(PartID,COND,sep = "_"),
+                         "_EventCodes.mat",sep = ""))
+
+EventData <- data.frame(Lat = unlist(mat$EventCodes$latency),
+                        Trig = mat$EventCodes$type)
+
+## Triggers of Interest; Stimulus codes, Target Codes, Response Codes
+TOI <- list()
+TOI[['Stim']] <- c("S  1","S  2","S  3")
+TOI[['Target']] <- c("S101","S102","S103",
+                     "S110","S112","S113",
+                     "S121","S120","S123",
+                     "S131","S132","S130")
+TOI[["Resp"]] <- c("S201","S202","S203") # The first participants have these codes
+                   # "S 73","S 74","S 75") # The px CLP130 had these codes
+TOI[["TrialEnd"]] <- "S 50"
+
+## Trigger codes are organised as follows:
+# Cue: 1 = Visual, 2 = Auditory, 3 = Ambiguous
+# Target: 1VA where V = Visual target, A = Auditory target
+# E.g., 123 = Visual Target indicating middle resp; Auditory Target indicating Right response
+# e.g., 101 = No Visual target; Auditory Target indicating Left response
+# Repsonse: 1 = Left, 2 = Middle, 3 = Right.
+
+
+## RT on trial one:
+CueCode  <- which(EventData$Trig %in% TOI[["Stim"]]) # pos. of Cue Trig Codes
+TargCode <- which(EventData$Trig %in% TOI[["Target"]]) # pos. of Target Trig Codes
+RespCode <- which(EventData$Trig %in% TOI[["Resp"]]) # pos. of Response Trig Codes
+ErrCheck <- which((TargCode+2) %in% RespCode)
+
+# Misses (omissions) are not recorded.
+# Instead the response code is positioned after the end of the trial
+# Likewise, some double presses are coded.
+
+## Create list with each trial as seperate dataframe
+TrialList <- list()
[…]

### 2020-05-13 Functions/Make_Table.R

@@ -1,0 +1,36 @@
+Make_Table <- function(rows,columns,measures,summ,BF.tests,delta.list){
+
+Table <- data.frame(matrix(nrow = length(sites), ncol = length(columns)))
+names(Table) <- columns
+Sum <- as.data.frame(summ[[measure]]) 
+Sum$name <- rownames(Sum)
+Table$Site <- paste(comp,gsub("StopSuccess_","",Sum %>% dplyr::filter(stringr::str_detect(name,pattern="StopSuccess")) %>% dplyr::filter(stringr::str_detect(name,pattern = sites)) %>% .$name),sep="_")
+Table$Measure <- measure
+# Table$t <- as.data.frame(t.tests[[measure]]) %>% filter(Variable=="statistic_t",site %in% rownames(Table)) %>% .$value
+# Table$pFDR <- as.data.frame(t.tests[[measure]]) %>% filter(Variable=="FDR_p_value",site %in% rownames(Table)) %>% .$value
+# # Table$df <- as.data.frame(t.tests[[measure]]) %>% filter(Variable=="parameter_df",site %in% rownames(Table)) %>% .$value
+for (i in 1:nrow(Table)){
+  Table$BF[[i]] <- BayesFactor::extractBF(BF.tests[[measure]][[gsub(paste(comp,"_",sep=""),"",Table$Site[[i]])]],logbf = F,onlybf = T)
+  
+}
+
+for ( i in 1:nrow(Table)){
+  Table$Delta[[i]] <- delta.list[[measure]][[gsub(paste(comp,"_",sep=""),"",Table$Site[[i]])]]
+  
+  
+}
+
+
+Table$SS <- round(Sum %>% filter(stringr::str_detect(name,pattern="StopSuccess")) %>% filter(stringr::str_detect(name,pattern = sites)) %>% .$mean,2)
+Table$SF <- round(Sum %>% filter(stringr::str_detect(name,pattern="StopFailure")) %>% filter(stringr::str_detect(name,pattern = sites)) %>% .$mean,2)
+
+Table$SS_sd <- round(Sum %>% filter(stringr::str_detect(name,pattern="StopSuccess")) %>% filter(stringr::str_detect(name,pattern = sites)) %>% .$std.dev,2)
[…]

### 2020-05-13 Functions/MethodsList.R

@@ -1,0 +1,146 @@
+MethodsList <- function(data) {
+  ## Calculate necessary variables and store in list:
+  
+  # # Summary of CTI
+  # meanCTI = mean(data$CTI, na.rm = T)
+  # sdCTI = sd(data$CTI, na.rm = T)
+  # # Summary of ITI
+  # meanITI = mean(data$ITI, na.rm = T)
+  # sdITI = sd(data$ITI, na.rm = T)
+  #
+  # # Percentage of Errors, Split by condition
+  # Errors_p = unlist(lapply(Subjidx_p, function(x)
+  #   nrow(data[data$PartID == x &
+  #                    data$Accuracy == "Error" &
+  #                    data$Condition == "p",]) / nrow(data[data$PartID == x &
+  #                                                                     data$Condition == "p",])))
+  # Errors_np = unlist(lapply(Subjidx, function(x)
+  #   nrow(data[data$PartID == x &
+  #                    data$Accuracy == "Error" &
+  #                    data$Condition == "np",]) / nrow(data[data$PartID == x &
+  #                                                                      data$Condition == "np",])))
+  # # Percentage of Misses, Split by condition
+  # Miss_p = unlist(lapply(Subjidx_p, function(x)
+  #   nrow(data[data$PartID == x &
+  #                    data$Accuracy == "Miss" &
+  #                    data$Condition == "p",]) / nrow(data[data$PartID == x &
+  #                                                                     data$Condition == "p",])))
+  # Miss_np = unlist(lapply(Subjidx, function(x)
+  #   nrow(data[data$PartID == x &
+  #                    data$Accuracy == "Miss" &
+  #                    data$Condition == "np",]) / nrow(data[data$PartID == x &
+  #                                                                      data$Condition == "np",])))
+  # # Errors by Visual Cue Type, Split by Condition
+  # Errors_p_Vis <- unlist(lapply(Subjidx_p, function(x)
+  #   nrow(data[data$PartID == x &
+  #                    data$Accuracy == "Error" &
+  #                    data$CueType == "Visual" &
+  #                    data$Condition == "p",]) / nrow(data[data$PartID == x &
+  #                                                                     data$CueType == "Visual" &
+  #                                                                     data$Condition == "p",])))
+  # Errors_np_Vis <- unlist(lapply(Subjidx, function(x)
+  #   nrow(data[data$PartID == x &
+  #                    data$Accuracy == "Error" &
[…]

### 2020-05-13 Functions/RTSum.R

@@ -1,0 +1,22 @@
+RTSum <- function(list, sublist, sublist_levels,subj){
+  RT   <- list()
+  
+  for (i in seq_along(subj)) {
+    ## Create a dummy variable to store participant level data
+    subjdummy <- list[[sublist]][list[[sublist]]$PartID == subj[i], ]
+    ## Loop through participants and apply a percentage to each level of the list
+    OmmRates[[i]] <-
+      lapply(sublist_levels, function(x)
+        (subjdummy$n[subjdummy[[sublist]] == x &
+                       subjdummy$Accuracy == "Miss"] / sum(subjdummy$n[subjdummy[[sublist]] == x])) * 100)
+    names(OmmRates[[i]]) <- sublist_levels
+    
+  names(OmmRates) <- subj
+  }
+  ## Transform into data frames
+  
+  ErrorRates.data <- do.call(rbind,ErrorRates)
+  
+  return(list(Errors = ErrorRates.data,
+              Ommissions = OmmRates.data))
+}

### 2020-05-13 Functions/RT_Plots.R

@@ -1,0 +1,608 @@
+# Create dataframes of within subject error
+wse <- list()
+#### Modality ####
+## Create summary using within subject data for error-bars
+wse[["TargetAccuracy"]] <- Rmisc::summarySEwithin(
+  Trialdata %>%
+    dplyr::filter(Accuracy!="Miss") %>%
+    dplyr::group_by(PartID, Target, Accuracy) %>% 
+    dplyr::summarise(RT = mean(RT,na.rm=T)),
+  measurevar = "RT",
+  withinvars = c("Target","Accuracy"),
+  idvar = "PartID",
+  na.rm = FALSE,
+  conf.interval = .95
+)
+
+wse[["TargetCondition"]] <- Rmisc::summarySEwithin(
+  Trialdata %>%
+    dplyr::filter(Accuracy!="Miss") %>% 
+    dplyr::group_by(PartID, Target, Condition) %>% 
+    dplyr::summarise(RT = mean(RT,na.rm=T)),
+  measurevar = "RT",
+  withinvars = c("Target","Condition"),
+  idvar = "PartID",
+  na.rm = FALSE,
+  conf.interval = .95
+)
+
+wse[["TargetPreparation"]] <- Rmisc::summarySEwithin(
+  Trialdata %>%
+    dplyr::filter(Accuracy!="Miss") %>% 
+    dplyr::group_by(PartID, Target, CueType) %>% 
+    dplyr::summarise(RT = mean(RT,na.rm=T)),
+  measurevar = "RT",
+  withinvars = c("Target","CueType"),
+  idvar = "PartID",
+  na.rm = FALSE,
+  conf.interval = .95
+)
+
+wse[["TargetDistractor"]] <- Rmisc::summarySEwithin(
+  Trialdata %>%
+    dplyr::filter(Accuracy!="Miss") %>% 
+    dplyr::group_by(PartID, Target, Distractor) %>% 
+    dplyr::summarise(RT = mean(RT,na.rm=T)),
+  measurevar = "RT",
+  withinvars = c("Target","Distractor"),
+  idvar = "PartID",
+  na.rm = FALSE,
+  conf.interval = .95
+)
+
+#### Preparation ####
+wse[["CueTypeAccuracy"]] <- Rmisc::summarySEwithin(
+  Trialdata %>%
+    dplyr::filter(Accuracy!="Miss") %>%
+    dplyr::group_by(PartID, CueType, Accuracy) %>% 
[…]

### 2020-05-13 Functions/TableFormat.R

@@ -1,0 +1,36 @@
+TableFormat <- function(data,VOI,columns){
+  Table <- data.frame(matrix(nrow = length(VOI), ncol = length(columns)))
+  names(Table) <- columns
+  Sum <- as.data.frame(summ[[measure]]) 
+  Sum$name <- rownames(Sum)
+  Table$Site <- paste(comp,gsub("StopSuccess_","",Sum %>% dplyr::filter(stringr::str_detect(name,pattern="StopSuccess")) %>% dplyr::filter(stringr::str_detect(name,pattern = sites)) %>% .$name),sep="_")
+  Table$Measure <- measure
+  # Table$t <- as.data.frame(t.tests[[measure]]) %>% filter(Variable=="statistic_t",site %in% rownames(Table)) %>% .$value
+  # Table$pFDR <- as.data.frame(t.tests[[measure]]) %>% filter(Variable=="FDR_p_value",site %in% rownames(Table)) %>% .$value
+  # # Table$df <- as.data.frame(t.tests[[measure]]) %>% filter(Variable=="parameter_df",site %in% rownames(Table)) %>% .$value
+  for (i in 1:nrow(Table)){
+    Table$BF[[i]] <- BayesFactor::extractBF(BF.tests[[measure]][[gsub(paste(comp,"_",sep=""),"",Table$Site[[i]])]],logbf = F,onlybf = T)
+    
+  }
+  
+  for ( i in 1:nrow(Table)){
+    Table$Delta[[i]] <- delta.list[[measure]][[gsub(paste(comp,"_",sep=""),"",Table$Site[[i]])]]
+    
+    
+  }
+  
+  
+  Table$SS <- round(Sum %>% filter(stringr::str_detect(name,pattern="StopSuccess")) %>% filter(stringr::str_detect(name,pattern = sites)) %>% .$mean,2)
+  Table$SF <- round(Sum %>% filter(stringr::str_detect(name,pattern="StopFailure")) %>% filter(stringr::str_detect(name,pattern = sites)) %>% .$mean,2)
+  
+  Table$SS_sd <- round(Sum %>% filter(stringr::str_detect(name,pattern="StopSuccess")) %>% filter(stringr::str_detect(name,pattern = sites)) %>% .$std.dev,2)
[…]

### 2020-07-06 ManuscriptMarkdown.Rmd
Further additions to methods

@@
 # # Install CRAN packages, if necessary
-if(sum(!Packages %in% rownames(installed.packages()))>=1){
-invisible(lapply(Packages,install.packages,dependencies=TRUE))
-}
+# if(sum(!Packages %in% rownames(installed.packages()))>=1){
+# invisible(lapply(Packages,install.packages,dependencies=TRUE))
+# }
 
@@
 ```{r Methods Set-up, echo=FALSE}
-Subjidx <- dir("../Data/")
-# Participant "CLP130" has a few problems. Including odd trigger codes. We'll rid ourselves of this participant for now.
-Subjidx <- Subjidx[-30]
+
+# As per the following document. Only CLP106 -> CLP 149 are useable
+PainCodes <- read.csv("EEGIdentity.csv")
+PainCodes$Subjidx <- paste("CLP",PainCodes$Subjidx,sep = "")
+
+Subjidx <- PainCodes$Subjidx
+
+# # Participant "CLP130" has a few problems. Including odd trigger codes. We'll rid ourselves of this participant for now.
+# Subjidx <- Subjidx[-30]
 
@@
 Trialdata <- read.csv("Output/TrialData.csv")
-Subjidx <- unique(Trialdata$PartID)
-## Some extreme CTI and ITI values were found. See plots
-# hist(Trialdata$CTI)
-# hist(Trialdata$ITI)
-# Participants 101,102,107 are clear outliers and appear to have some extra long CTIs
+Trialdata <- Trialdata[Trialdata$PartID %in% Subjidx,]
+
+## check CTI and ITI values:
+hist(Trialdata$CTI)
+hist(Trialdata$ITI)
+table(Trialdata$PartID[Trialdata$ITI>4000]) # CLP124 might need a look into for long ITIs
 
@@
 source('Functions/MethodsList.R')
-Summdata <- MethodsList(Trialdata)
+Summdata <- MethodsList(Trialdata) # Can ignore warnings - RE: meaning RT for miss trials/SD for 2 trials total
 ```
@@
 ## 2.1. Participants
-  A total of `r length(unique(Summdata$PartID))` participants were recruited for the study.
-They were recruited from *Insert here* and ranged in age from *X-Xyrs (X% Female)*.
+  A total of *XXX* participants were recruited for the study, recruited from *Insert here*.
+A total of `r length(unique(Summdata$PartID))` participants remained after data cleaning and exclusion as outlined below.
+These participants ranged in age from *X-Xyrs (mean +/- SD) and were X% Female*.
 The study confirmed to ethics approved by *Ethics board of study*.
@@
 
-### 2.2.X. Cross-modal Attention task
+### 2.2.1. Cross-modal Attention task
 
@@
 Some have maxes of ~800ms and min of ~700ms.
-Others (N = 3) have max ~1500 and min ~1400*).
-Each trial lasted approximately `r round(mean(Trialdata %>% group_by(PartID) %>% summarise(meanITI = mean(ITI,na.rm=T)) %>% .$meanITI),0)`, with a jitter of **XXX** (*Again, same three participants throw this estimate out*).
+Others (N = 3) have max ~1500 and min ~1400* **I beleive I have fixed this with removal of some px**).
+Each trial lasted approximately `r round(mean(Trialdata %>% group_by(PartID) %>% summarise(meanITI = mean(ITI,na.rm=T)) %>% .$meanITI),0)`, with a jitter of **XXX**.
+
+### 2.2.2. EEG Recording
+  Participants completed the aforementioned task with concurent EEG recording using a **XXXX** system, fitted to the standard 10-20 system.
+EEG was sampled at 500Hz and referenced to referenced to the Afz electrode.
+Peripheral recordings of galvantic skin conductance, heart rate, and respiration were taken.
+
+## 2.3. Data Extraction
+### 2.3.1. Behaivoural Data
+  The extracted variables from the beahvioural data include mean and standard deviation of correct reaction times (RT), mean and standard deviation of erronous reaction times (RT~err~), percentage of errors of comission, percentage of omission errors.
+For each condition (i.e., No-pain vs Pain) these variables were extracted across the following groupings; Modality (Visual vs Auditory cues), Preparation (Cued vs Ambiguous trials), and Distraction (Present vs Absent distractors).
+
+### 3.3.2. EEG Data
+```{r EEG summary}
+## Calculate the summary stats of the EEG analysis. RE: trial counts, channel/component removal
+
+# Read in data from .mat files
+
+# Summarise number of removed channels
+
+# Summarise number of removed components
+
+# Summarise number of removed trials
+
+# Summarise the average total number of trials for each condition
+
+```
+  An outline of the EEG pre-processing undertaken here is presented in Figure *X*.
+EEG data were first average referenced and high pass filtered at 1Hz using the *removeTrend* function.
+Line noise of 6Hz and its associated harmonics was removed using a notch filter before the *clean_artifacts* function was used to detect bad channels.
+Channels were marked for removal is there was noise greater than 4 standard deviations greater than the mean, 1/5th of the channel was flat, or correlations with other channels was lower than .8.
+This processed removed an average of **XX** +/- **XX** of channels.
+The results of this were visually inspected ad confirmed before data was subjected to ICA.
+Resulting components from the *run_ica* output was marked for removal with the the ICLabel algorthm, where compnents classifed greater than 75% eye, greater than 80% muscle, or greater than 90% heart, line, and channel were removed.
+Visual inspection confirmed the component removal and the ICA weights were saved for later referral.
+  The final EEG data set was high pass filtered at 0.1Hz.
+Bad channels were removed and ICA weights were added to the data and bad components removed.
+An average of **XX** +/- **XX** copmonents were removed for each participant.
+Channels were then interpolated using *pop_interp* and data epoched 1.5s before the cue to 2.5s post-cue, for each cue seperately.
+EEGLABs extreme epoch noise detection using EEGLab's threshold & joint probability procedures was undertaken with the cut-off for amplitude set at 100uV **put in other stuff heree**.
+An average of **XX** +/- **XX** trials were removed using this procedure for each participant.
+Lastly, data were current source density transformed useing Fieldtrips *ft_scalpcurrentdensity* using the spline method.
+  An average of **XX** +/- trials remained for each participant.
+Visual and auditory cued trials made up XX% of these trials, matching the original paradigm setting of XX%.
+Time freqeucny transform was undertaken closely following the advice of Cohen (2014; *check refrence*).
+In short, Morelt wavelets were created at different frequency dependent widths.
+Across the 80 linearlly spaced frequency bins between 3 and 30Hz, wavelets were created with widths between 6 and 10 cycles.
+In other words, smaller width wavelets were used for slower frequencies and larger width wavelets were used for faster frequncies.
+This allowed for the investigation of multiple freqency bands (i.e., both Theta and Alpha) with approximately the same resolution.
+The output of this process was baselined using a decibel conversion to the time period -500 to -200ms pre-cue.
+ERPs to each cue were taken for the time period up to 1 second post cue.
+To control for high frequency noise, the data were low pass filtered at 30Hz for the ERP analyis.
+ERPs were baselined -200ms to cue onset (i.e., 0ms).
+
+## 2.4. Statistical Procedure
+### 2.4.1. Behavioural Analysis
+**UPDATE**
+  The behavioural data of the C-MAT task was first assessed in the no pain condition.
+To explore the influence of Modality, Preparation, and Distraction, a large Bayesian ANOVA model comparing each of these was established.
+Models were run on correct reaction times.
+However, as error and omission rates were overall low and absent in some participants, these effects should be treated with caution.
+  To test the presence or absence of an effect we first examined the overall best fit model by examining Bayes Factors of each model respective to the null model.
+If interactions were present we also assessed the inclusion Bayes Factor, by controlling for simple effects of the interaction.
+The BF~inclusion~ described the evidence for the inclusion of a specific factor of the model.
+The influence of pain on the aformentioned effects is then assesed by adding a Pain (No-Pain vs.
+Pain) factor to the overall model.
+
+### 2.4.2. EEG Analysis
 
@@
 }
-tmp =load(file = "Output/RT_Plots.RData")
+tmp = load(file = "Output/RT_Plots.RData")
 
@@
 ```
+
 ## 3.1. Behavioural Results

### 2020-07-09 ManuscriptMarkdown.Rmd
EEG Preprocessing SUmmary stats

@@
 ```{r Methods Set-up, echo=FALSE}
-
 # As per the following document. Only CLP106 -> CLP 149 are useable
@@
 
-Subjidx <- PainCodes$Subjidx
+Subjidx <- dir(path = "Data/RejectData/",
+               pattern = "CLP*")
+# Remove CLP116_2 until we know what that's about.
+Subjidx <- Subjidx[Subjidx != "CLP116_2"]
 
-# # Participant "CLP130" has a few problems. Including odd trigger codes. We'll rid ourselves of this participant for now.
-# Subjidx <- Subjidx[-30]
+# Seperate into those with pain data and those without
+pain_Subjidx <- Subjidx[unlist(
+  lapply(Subjidx, function(px)
+    file.exists(
+      paste("Data/RejectData/", px, "/", px, "_p_BadChannels.txt",sep = "")
+    )))]
+
+# Reduce particpants down to finalised numbers
+PainCodes <- PainCodes[PainCodes$Subjidx %in% Subjidx,]
 
@@
 hist(Trialdata$ITI)
-table(Trialdata$PartID[Trialdata$ITI>4000]) # CLP124 might need a look into for long ITIs
+table(Trialdata$PartID[Trialdata$ITI>4000]) # CLP114 and CLP124 might need a look into for long ITIs
 
@@
 source('Functions/MethodsList.R')
-Summdata <- MethodsList(Trialdata) # Can ignore warnings - RE: meaning RT for miss trials/SD for 2 trials total
+Summdata <- MethodsList(Trialdata) # Can ignore warnings - RE: mean RT for miss trials/SD for 2 trials total
 ```
@@
 ## Calculate the summary stats of the EEG analysis. RE: trial counts, channel/component removal
+EEGPreProc <- list()
+# Read in data from .txt files
+EEGPreProc[["BadChan"]] <- list()
 
-# Read in data from .mat files
+## Collate number of removed channels
+EEGPreProc[["BadChan"]][["np"]] <- lapply(Subjidx,
+                                          function(px)
+                                            nrow(
+                                              read.table(
+                                                paste("Data/RejectData/",
+                                                      px, "/",
+                                                      px,
+                                                      "_np_BadChannels.txt",
+                                                      sep = ""),
+                                                row.names = NULL,
+                                                quote = "\"",
+                                                comment.char = ""
+                                              )
+                                            ))
 
-# Summarise number of removed channels
+names(EEGPreProc[["BadChan"]][["np"]]) <- Subjidx
 
-# Summarise number of removed components
+EEGPreProc[["BadChan"]][["p"]] <- lapply(pain_Subjidx,
+                                         function(px)
+                                           nrow(
+                                             read.table(
+                                               paste("Data/RejectData/",
+                                                     px, "/",
+                                                     px,
+                                                     "_p_BadChannels.txt",
+                                                     sep = ""),
+                                               row.names = NULL,
+                                               quote = "\"",
+                                               comment.char = ""
+                                             )
+                                           ))
 
-# Summarise number of removed trials
+names(EEGPreProc[["BadChan"]][["p"]]) <- pain_Subjidx
 
-# Summarise the average total number of trials for each condition
+# Both conditions together
+EEGPreProc[["BadChan"]][["Both"]] <- setNames(mapply(c, EEGPreProc[["BadChan"]][["np"]][Subjidx], EEGPreProc[["BadChan"]][["p"]][Subjidx]), Subjidx)
+
+# Both conditions averaged
+EEGPreProc[["BadChan"]][["Average"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["BadChan"]][["Both"]][[x]]))
+
+## Summarise number of removed components
+EEGPreProc[["RejComp"]][["np"]] <- lapply(Subjidx,
+                                          function(px)
+                                            nrow(
+                                              read.table(
+                                                paste("Data/RejectData/",
+                                                      px, "/",
+                                                      px,
+                                                      "_np_RejectedComps.txt",
+                                                      sep = ""),
+                                                row.names = NULL,
+                                                quote = "\"",
+                                                comment.char = ""
+                                              )
+                                            ))
+
+names(EEGPreProc[["RejComp"]][["np"]]) <- Subjidx
+
+EEGPreProc[["RejComp"]][["p"]] <- lapply(pain_Subjidx,
+                                         function(px)
+                                           nrow(
+                                             read.table(
+                                               paste("Data/RejectData/",
+                                                     px, "/",
+                                                     px,
+                                                     "_p_RejectedComps.txt",
+                                                     sep = ""),
+                                               row.names = NULL,
+                                               quote = "\"",
+                                               comment.char = ""
+                                             )
+                                           ))
+
+names(EEGPreProc[["RejComp"]][["p"]]) <- pain_Subjidx
+
+# Both conditions together
+EEGPreProc[["RejComp"]][["Both"]] <- setNames(mapply(c, EEGPreProc[["RejComp"]][["np"]][Subjidx], EEGPreProc[["RejComp"]][["p"]][Subjidx]), Subjidx)
+
+# Both conditions averaged
+EEGPreProc[["RejComp"]][["Average"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejComp"]][["Both"]][[x]]))
+
+## Summarise number of removed trials
+EEGPreProc[["RejTrial"]][["np"]][["Visual"]] <- lapply(Subjidx,
+                                                       function(px)
+                                                         read.table(
+                                                           paste(
+                                                             "Data/RejectData/",
+                                                             px,
+                                                             "/",
+                                                             px,
+                                                             "_np_RF_Proc_RejTrials.txt",
+                                                             sep = ""
+                                                           ),
+                                                           row.names = NULL,
+                                                           quote = "\"",
+                                                           comment.char = ""
+                                                         )[[1, 1]])
+
+names(EEGPreProc[["RejTrial"]][["np"]][["Visual"]]) <- Subjidx
+
+EEGPreProc[["RejTrial"]][["np"]][["Auditory"]] <- lapply(Subjidx,
+                                                       function(px)
+                                                         read.table(
+                                                           paste(
+                                                             "Data/RejectData/",
+                                                             px,
+                                                             "/",
+                                                             px,
+                                                             "_np_RF_Proc_RejTrials.txt",
+                                                             sep = ""
+                                                           ),
+                                                           row.names = NULL,
+                                                           quote = "\"",
+                                                           comment.char = ""
+                                                         )[[2, 1]])
+
+names(EEGPreProc[["RejTrial"]][["np"]][["Auditory"]]) <- Subjidx
+
+EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]] <- lapply(Subjidx,
+                                                       function(px)
+                                                         read.table(
+                                                           paste(
+                                                             "Data/RejectData/",
+                                                             px,
+                                                             "/",
+                                                             px,
+                                                             "_np_RF_Proc_RejTrials.txt",
+                                                             sep = ""
+                                                           ),
+                                                           row.names = NULL,
+                                                           quote = "\"",
+                                                           comment.char = ""
+                                                         )[[3, 1]])
+
+names(EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]]) <- Subjidx
+
+EEGPreProc[["RejTrial"]][["p"]][["Visual"]] <- lapply(pain_Subjidx,
+                                                       function(px)
+                                                         read.table(
+                                                           paste(
+                                                             "Data/RejectData/",
+                                                             px,
+                                                             "/",
+                                                             px,
+                                                             "_p_RF_Proc_RejTrials.txt",
+                                                             sep = ""
+                                                           ),
+                                                           row.names = NULL,
+                                                           quote = "\"",
+                                                           comment.char = ""
+                                                         )[[1, 1]])
+
+names(EEGPreProc[["RejTrial"]][["p"]][["Visual"]]) <- pain_Subjidx
+
+EEGPreProc[["RejTrial"]][["p"]][["Auditory"]] <- lapply(pain_Subjidx,
+                                                       function(px)
+                                                         read.table(
+                                                           paste(
+                                                             "Data/RejectData/",
+                                                             px,
+                                                             "/",
+                                                             px,
+                                                             "_p_RF_Proc_RejTrials.txt",
+                                                             sep = ""
+                                                           ),
+                                                           row.names = NULL,
+                                                           quote = "\"",
+                                                           comment.char = ""
+                                                         )[[2, 1]])
+
+names(EEGPreProc[["RejTrial"]][["p"]][["Auditory"]]) <- pain_Subjidx
+
+EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]] <- lapply(pain_Subjidx,
+                                                       function(px)
+                                                         read.table(
+                                                           paste(
+                                                             "Data/RejectData/",
+                                                             px,
+                                                             "/",
+                                                             px,
+                                                             "_p_RF_Proc_RejTrials.txt",
+                                                             sep = ""
+                                                           ),
+                                                           row.names = NULL,
+                                                           quote = "\"",
+                                                           comment.char = ""
+                                                         )[[3, 1]])
+
+names(EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]]) <- pain_Subjidx
+
+# Both conditions together
+EEGPreProc[["RejTrial"]][["Both"]][["Visual"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Visual"]][Subjidx],                                                       EEGPreProc[["RejTrial"]][["p"]][["Visual"]][Subjidx]), Subjidx)
+
+EEGPreProc[["RejTrial"]][["Both"]][["Auditory"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Auditory"]][Subjidx], EEGPreProc[["RejTrial"]][["p"]][["Auditory"]][Subjidx]), Subjidx)
+
+EEGPreProc[["RejTrial"]][["Both"]][["Ambiguous"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]][Subjidx], EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]][Subjidx]), Subjidx)
+
+# Both conditions averaged
+EEGPreProc[["RejTrial"]][["Average"]][["Visual"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Visual"]][[x]]))
+
+EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Auditory"]][[x]]))
+
+EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Ambiguous"]][[x]]))
+
+## Total Trials
+sum(EEGPreProc[["RejTrial"]][["Average"]][["Visual"]][[1]],
+    EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]][[1]],
+    EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]][[1]])
 
@@
 Channels were marked for removal is there was noise greater than 4 standard deviations greater than the mean, 1/5th of the channel was flat, or correlations with other channels was lower than .8.
-This processed removed an average of **XX** +/- **XX** of channels.
+This processed removed an average of `r round(mean(unlist(EEGPreProc$BadChan$Average)),0)` +/- `r round(sd(unlist(EEGPreProc$BadChan$Average)),0)` of channels.
 The results of this were visually inspected ad confirmed before data was subjected to ICA.
@@
 Bad channels were removed and ICA weights were added to the data and bad components removed.
-An average of **XX** +/- **XX** copmonents were removed for each participant.
+An average of `r round(mean(unlist(EEGPreProc$RejComp$Average)),0)` +/- `r round(sd(unlist(EEGPreProc$RejComp$Average)),0)` copmonents were removed for each participant.
 Channels were then interpolated using *pop_interp* and data epoched 1.5s before the cue to 2.5s post-cue, for each cue seperately.
 EEGLABs extreme epoch noise detection using EEGLab's threshold & joint probability procedures was undertaken with the cut-off for amplitude set at 100uV **put in other stuff heree**.
-An average of **XX** +/- **XX** trials were removed using this procedure for each participant.
+An average of `r round(mean(unlist(EEGPreProc$RejTrial$Average)),0)` +/- `r round(sd(unlist(EEGPreProc$RejTrial$Average)),0)` trials were removed using this procedure for each participant.
 Lastly, data were current source density transformed useing Fieldtrips *ft_scalpcurrentdensity* using the spline method.

### 2020-07-16 ManuscriptMarkdown.Rmd
Improved plotting scripts

@@
 .libPaths("./Packages")
-Packages <- c("ggplot2","dplyr","reshape",#"wesanderson",
+Packages <- c("ggplot2","dplyr","reshape","wesanderson",
               "BayesFactor",
               "kableExtra","rmatio","Rmisc",
-              "rmarkdown","data.table","devtools") # Slew of packages used here.
+              "rmarkdown","data.table","devtools",
+              "cowplot","dplyr","readr") # Slew of packages used here.
 
@@
 }
+
+## Raincloud plot function
+source("./Packages/RainCloudPlots-master/tutorial_R/R_rainclouds.R")
 
@@
 ### 2.3.1. Behaivoural Data
-  The extracted variables from the beahvioural data include mean and standard deviation of correct reaction times (RT), mean and standard deviation of erronous reaction times (RT~err~), percentage of errors of comission, percentage of omission errors.
-For each condition (i.e., No-pain vs Pain) these variables were extracted across the following groupings; Modality (Visual vs Auditory cues), Preparation (Cued vs Ambiguous trials), and Distraction (Present vs Absent distractors).
+  The extracted variables from the beahvioural data include mean and standard deviation of correct reaction times (RT), mean and standard deviation of erronous reaction times (RT~err~), percentage of errors of comission, and percentage of omission errors.
+For each condition (i.e., No-pain and Pain) these variables were extracted across the following groupings; Modality (Visual vs Auditory cues), Preparation (Cued vs Ambiguous trials), and Distraction (Present vs Absent distractors).
 
@@
 # Read in data from .txt files
-EEGPreProc[["BadChan"]] <- list()
 
@@
 
-## Total Trials
-sum(EEGPreProc[["RejTrial"]][["Average"]][["Visual"]][[1]],
-    EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]][[1]],
-    EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]][[1]])
+## Total Trials Removed
+EEGPreProc[["RejTrial"]][["Total"]] <- lapply(seq_along(Subjidx),
+                                              function(x)
+                                              sum(EEGPreProc[["RejTrial"]][["Average"]][["Visual"]][[x]],
+                                              EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]][[x]],
+                                              EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]][[x]]))
 
+Perc_TrialsRemoved <- data.frame(Vis = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Visual"]])/120),
+                            Aud = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]])/120),
+                            Amb = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]])/60))
+## Compare Cue Types on the percentage of removed trials
+# format data
+TrialsRemoved_test <- reshape2::melt(Perc_TrialsRemoved)
+# Freq test
+TR_ANOVA <- aov(value ~ variable, data = TrialsRemoved_test)
+# Bayes test
+BF_TR_ANOVA <- BayesFactor::anovaBF(value ~ variable, data = TrialsRemoved_test)
 ```
@@
 Channels were marked for removal is there was noise greater than 4 standard deviations greater than the mean, 1/5th of the channel was flat, or correlations with other channels was lower than .8.
-This processed removed an average of `r round(mean(unlist(EEGPreProc$BadChan$Average)),0)` +/- `r round(sd(unlist(EEGPreProc$BadChan$Average)),0)` of channels.
+This processed removed an average of `r round(mean(unlist(EEGPreProc$BadChan$Average)),2)` +/- `r round(sd(unlist(EEGPreProc$BadChan$Average)),2)` of channels.
 The results of this were visually inspected ad confirmed before data was subjected to ICA.
@@
 Bad channels were removed and ICA weights were added to the data and bad components removed.
-An average of `r round(mean(unlist(EEGPreProc$RejComp$Average)),0)` +/- `r round(sd(unlist(EEGPreProc$RejComp$Average)),0)` copmonents were removed for each participant.
+An average of `r round(mean(unlist(EEGPreProc$RejComp$Average)),2)` +/- `r round(sd(unlist(EEGPreProc$RejComp$Average)),2)` copmonents were removed for each participant.
 Channels were then interpolated using *pop_interp* and data epoched 1.5s before the cue to 2.5s post-cue, for each cue seperately.
 EEGLABs extreme epoch noise detection using EEGLab's threshold & joint probability procedures was undertaken with the cut-off for amplitude set at 100uV **put in other stuff heree**.
-An average of `r round(mean(unlist(EEGPreProc$RejTrial$Average)),0)` +/- `r round(sd(unlist(EEGPreProc$RejTrial$Average)),0)` trials were removed using this procedure for each participant.
+An average of `r round(mean(unlist(EEGPreProc$RejTrial$Average)),2)` +/- `r round(sd(unlist(EEGPreProc$RejTrial$Average)),2)` trials were removed using this procedure for each participant.
 Lastly, data were current source density transformed useing Fieldtrips *ft_scalpcurrentdensity* using the spline method.
-  An average of **XX** +/- trials remained for each participant.
-Visual and auditory cued trials made up XX% of these trials, matching the original paradigm setting of XX%.
+  An average of `r round(mean(unlist(EEGPreProc[["RejTrial"]][["Total"]])),2)` +/- `r round(sd(unlist(EEGPreProc[["RejTrial"]][["Total"]])),2)` trials were removed for each participant.
+There was no influence of Cue Type on the percentage of trials removed, as shown with a one-way ANOVA (`r papaja::apa_print.aov(TR_ANOVA)$full_result$variable`).
+An equivilant Bayesian ANOVA showed evidence for the null (BF~10~ = `r round(extractBF(BF_TR_ANOVA)[[1]],3)`).
   Time freqeucny transform was undertaken closely following the advice of Cohen (2014; *check refrence*).
@@
 ### 2.4.1. Behavioural Analysis
-**UPDATE**
   The behavioural data of the C-MAT task was first assessed in the no pain condition.
 To explore the influence of Modality, Preparation, and Distraction, a large Bayesian ANOVA model comparing each of these was established.
-Models were run on correct reaction times.
-However, as error and omission rates were overall low and absent in some participants, these effects should be treated with caution.
-  To test the presence or absence of an effect we first examined the overall best fit model by examining Bayes Factors of each model respective to the null model.
-If interactions were present we also assessed the inclusion Bayes Factor, by controlling for simple effects of the interaction.
-The BF~inclusion~ described the evidence for the inclusion of a specific factor of the model.
+As error and omission rates were low overall and absent in some participants, these effects should be treated with caution.
+To test the presence or absence of an effect we first examined the overall best fit model by examining Bayes Factors of each model respective to the null model, which just includes a subject factor.
+If interactions are present we also assess the inclusion Bayes Factor, by controlling for matched models.
+The BF~inclusion~ describes the evidence for the inclusion of a specific factor (i.e., interaction) of the model, when controlling for the main effects.
+Any interactions were then explore using either one-way ANOVAs, or t-tests.
 The influence of pain on the aformentioned effects is then assesed by adding a Pain (No-Pain vs.
-Pain) factor to the overall model.
+Pain) factor to the overall model and exploring any possible interactions with the Pain factor using the aforementioned steps.
 
@@
 
+### 2.4.3. Determination of Effects
+  This study useses a joint methodology of frequentist and Bayesian tests.
+Bayesian tests are preferred and used where ever possible.
+However, as some common methodologies used in this literature have not been adapted to Bayesian, we use frequentist statistics alonside the Bayesian tests.
+For example, cluster based permutations are often used in the high dimensionality space of EEG, where multiple electrodes, across multiple subjects are compared across time-frequency space.
+The method itself helps control for multiple comparisons, which to date has not been as effectively and efficiently implimented in Bayes.
+
+  *Another option is to do a linear model*
+  For the ANOVA models on behavioural data with the default priors of Rouder, et al., (2012) and a 'medium' r scale of sqrt(2)/2. For *t-tests, blah blah is used...*
+  Evidence cut-offs are used to assist in interpretation of Bayes factors.
+In line with Kass & Rafferty, (1995), we use the following cut-offs.
+A Bayes factor between 1/3 and 3 is considered ‘Equivocal’ (i.e., indicating more data are needed to obtain a clear outcome), between 1/20–1/3 and 3–20 is considered ‘Positive’, between 1/150–1/20 and 20–150 ‘Strong’, and Bayes factors < 1/150 and > 150 are considered ‘Very Strong’.
+
 # 3. Results 
+  Blah blah we first present yada yada
 ```{r Results Set-up, echo=FALSE}
+#### Plotting RT ####
 ## Create plots to observe possible outliers, effects, interactions etc
 
-## Colour-blind friendly pallatte
+## Colour-blind friendly pallatte - I use wesanderson for plotting, colour blind friendly for pubs
 cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7","#000000")
@@
 ## We will plot four main comparisons on RT:
-# Modality (Auditory vs Visual targets)
-# Preparation (Cued-targets vs Ambiguous Target)
-# Interference/Distraction (Prescence vs Abscence of Targets)
-# Pain (Pain vs No-Pain conditions) - which will be compared across all of the above.
-if(!file.exists("Output/RT_Boxplots.pdf")){
-  source("Functions/RT_Plots.R")
+# Modality (Auditory vs Visual Targets)
+# Preparation (Cued-targets vs Ambiguous Target; i.e., CueType)
+# Interference/Distraction (Prescence vs Abscence of Targetsl; i.e., Distractor)
+# Pain (Pain vs No-Pain; ie., Condition) - Compared across all of the above.
+
+# source the function
+source('Functions/RT_RainPlots.R')
+
+# Change condition labels to plot better
+levels(Trialdata$Condition) <- c("No Pain","Pain")
+
+# Create list and loop through plots
+if(!file.exists("Output/RT_Rainplots.RData")){
+Plots <- list()
+RT_comp_xvals <- c("Target","CueType","Distractor","Condition")
+RT_comp_groupvals <- c("Accuracy","Target","CueType","Distractor","Condition")
+
+for (i in seq_along(RT_comp_xvals)){
+Plots[[RT_comp_xvals[i]]] <- lapply(RT_comp_groupvals,function(x) RT_RainPlot(data = Trialdata,
+                                                                      xval = RT_comp_xvals[i],
+                                                                      groupval = x))
+names(Plots[[RT_comp_xvals[i]]]) <- RT_comp_groupvals
 }
-tmp = load(file = "Output/RT_Plots.RData")
+save(Plots,file = "Output/RT_Rainplots.RData")
+
+}
+# Else we just load the data - much faster
+tmp = load(file = "Output/RT_Rainplots.RData")
 
@@
 
-# Create list of error rates splits of interest
+# Create list of error rates on splits of interest
 N_Trials <- list()
-N_Trials[["Condition"]] <- Trialdata %>% dplyr::group_by(PartID,Condition,Accuracy) %>%  dplyr::tally()
+N_Trials[["Condition"]] <-
+Trialdata %>% dplyr::group_by(PartID, Condition, Accuracy) %>% dplyr::tally() %>% dplyr::group_by(PartID,Condition) %>% dplyr::mutate(total = sum(n)) %>% dplyr::mutate(perc = (n/total)*100) %>% dplyr::select(-n,-total) %>% dplyr::filter(Accuracy!="Correct")
 
-N_Trials[["CueType"]] <- Trialdata %>% dplyr::group_by(PartID,CueType,Accuracy) %>%  dplyr::tally()
+N_Trials[["CueType"]] <-
+Trialdata %>% dplyr::group_by(PartID, CueType, Accuracy) %>% dplyr::tally() %>% dplyr::group_by(PartID,CueType) %>% dplyr::mutate(total = sum(n)) %>% dplyr::mutate(perc = (n/total)*100) %>% dplyr::select(-n,-total) %>% dplyr::filter(Accuracy!="Correct")
 
-N_Trials[["Distractor"]] <- Trialdata %>% dplyr::group_by(PartID,Distractor,Accuracy) %>%  dplyr::tally()
+N_Trials[["Distractor"]] <-
+Trialdata %>% dplyr::group_by(PartID, Distractor, Accuracy) %>% dplyr::tally() %>% dplyr::group_by(PartID,Distractor) %>% dplyr::mutate(total = sum(n)) %>% dplyr::mutate(perc = (n/total)*100) %>% dplyr::select(-n,-total) %>% dplyr::filter(Accuracy!="Correct")
 
-N_Trials[["Target"]] <- Trialdata %>% dplyr::group_by(PartID,Target,Accuracy) %>% dplyr::tally()
+N_Trials[["Target"]] <-
+Trialdata %>% dplyr::group_by(PartID, Target, Accuracy) %>% dplyr::tally() %>% dplyr::group_by(PartID,Target) %>% dplyr::mutate(total = sum(n)) %>% dplyr::mutate(perc = (n/total)*100) %>% dplyr::select(-n,-total) %>% dplyr::filter(Accuracy!="Correct")
 
-source('Functions/ErrRates.R')
+## Plot Errors and Omissions Data
+# Create list and loop through plots
+source('Functions/Error_RainPlots.R')
+if(!file.exists("Output/Errors_Rainplots.RData")){
+Error_comp_xvals <- "Accuracy"
+Error_comp_groupvals <- c("Target","CueType","Distractor","Condition")
 
-Errors_list <- list()
-for (i in seq_along(names(N_Trials))) {
-  Errors_list[[names(N_Trials)[[i]]]] <- ErrRates(
-    list = N_Trials,
-    sublist = names(N_Trials)[[i]],
-    sublist_levels = unique(N_Trials[[names(N_Trials)[[i]]]][[names(N_Trials)[[i]]]]),
-    subj = Subjidx
-  )
+Err_Plots <- lapply(Error_comp_groupvals, function(x)
+  Err_RainPlot(
+  data = N_Trials[[x]],
+  xval = "Accuracy",
+  groupval = x
+  ))
+  names(Err_Plots) <- Error_comp_groupvals
+
+  save(Err_Plots, file = "Output/Errors_Rainplots.RData")
 }
 
-## Build Errors data.frame ##
-Errorsdata <-
-  data.frame(lapply(names(Errors_list), function(x)
-    data.frame(Errors_list[[x]][["Errors"]])))
-# Turns the length = 0 lists into NA and creates data.frame
-for (i in names(Errorsdata)){
-      Errorsdata[[i]] <- unlist(ifelse(sapply(Errorsdata[[i]], length) == 0, NA, Errorsdata[[i]]))
-}
-names(Errorsdata) <- c("NoPain","Pain",
-                       "AmbiguousCue","AuditoryCue","VisualCue",
-                       "DistractorAbsent","DistractorPresent",
-                       "AuditoryTarget","VisualTarget")
-# Build Misses data frame #
-Missdata   <-
-  data.frame(lapply(names(Errors_list), function(x)
-    data.frame(Errors_list[[x]][["Ommissions"]])))
+# Else we just load the data - much faster
+tmp = load(file = "Output/Errors_Rainplots.RData")
 
-# Turns the length = 0 lists into NA and creates data.frame
-for (i in names(Missdata)){
-      Missdata[[i]] <- unlist(ifelse(sapply(Missdata[[i]], length) == 0, NA, Missdata[[i]]))
-}
-names(Missdata) <- c("NoPain","Pain",
-                       "AmbiguousCue","AuditoryCue","VisualCue",
-                       "DistractorAbsent","DistractorPresent",
-                       "AuditoryTarget","VisualTarget")
-# Clean as we go
-rm(Errors_list)
-
-## Create SPSS/JASP ready dataframe
-# RT column with one column for each interaction of variables
-SPSSdata <-
+## Create SPSS/JASP ready dataframe for RT
+Programdata <-
   reshape2::dcast(
-    data = Trialdata %>% dplyr::filter(Accuracy != "Miss"),
+    data = Trialdata,
     formula = PartID ~ Condition + CueType + Target + Distractor + Accuracy,
@@
 )
+
 # Write to file
-write.csv(SPSSdata, file = "Output/SPSSdata.csv",
+write.csv(Programdata, file = "Output/Wide_RTdata.csv",
           row.names = F)
 
-# Error rates
-# Write to file
-SPSSdata <-
-  reshape2::dcast(
-    data = Errorsdata,
-    formula = PartID ~ Condition + CueType + Target + Distractor,
-    fun.aggregate = mean,
-    value.var = "ErrorRates"
+## Create SPSS/JASP ready dataframe for errors
+N_Trials[["CueType"]]$CueType <- paste(N_Trials[["CueType"]]$CueType,"Cue",sep="")
+N_Trials[["Condition"]]$Condition <- as.character(N_Trials[["Condition"]]$Condition)
+N_Trials[["Distractor"]]$Distractor <- as.character(N_Trials[["Distractor"]]$Distractor)
+N_Trials[["Target"]]$Target <- as.character(N_Trials[["Target"]]$Target)
+
+for (i in seq_along(N_Trials)){
+  names(N_Trials[[i]]) <- c("PartID","Variable","Accuracy","Perc")
+}
+
+## Way too difficult way to create data frame
+Errorsdata <- data.frame(PartID = c(as.character(N_Trials$Condition$PartID),
+                                    as.character(N_Trials$CueType$PartID),
+                                    as.character(N_Trials$Distractor$PartID),
+                                    as.character(N_Trials$Target$PartID)),
+                         Variable = c(as.character(N_Trials$Condition$Variable),
+                                    as.character(N_Trials$CueType$Variable),
+                                    as.character(N_Trials$Distractor$Variable),
+                                    as.character(N_Trials$Target$Variable)),
+                         Accuracy = c(as.character(N_Trials$Condition$Accuracy),
+                                    as.character(N_Trials$CueType$Accuracy),
+                                    as.character(N_Trials$Distractor$Accuracy),
+                                    as.character(N_Trials$Target$Accuracy)),
+                         Perc = c(N_Trials$Condition$Perc,
+                                    N_Trials$CueType$Perc,
+                                    N_Trials$Distractor$Perc,
+                                    N_Trials$Target$Perc)
                          )
-write.csv(SPSSdata, file = "Output/Error_SPSSdata.csv",
-          row.names = F)
 
-write.csv(Errorsdata, file = "Output/Errors_data.csv",
-          row.names = F)
-# Ommissions rates
-# Write to file
-SPSSdata <-
-  reshape2::dcast(
-    data = Errorsdata,
-    formula = PartID ~ Condition + CueType + Target + Distractor,
-    fun.aggregate = mean,
-    value.var = "MissRates"
-  )
-write.csv(SPSSdata, file = "Output/Miss_SPSSdata.csv",
-          row.names = F)
-
-write.csv(Missdata, file = "Output/Miss_data.csv",
-          row.names = F)
 ```
@@
 ```{r Table 1, echo=FALSE}
-T1mean <- list()
-# Mean RT
-T1mean[["All"]] <-
-  aggregate(RT ~ PartID + Condition + CueType + Target + Distractor + Accuracy,
-            data = Trialdata,
-            FUN = mean)
-T1mean[["Modality"]] <- aggregate(RT ~ PartID + Target,
-            data = Trialdata,
-            FUN = mean)
-T1mean[["Preparation"]] <- aggregate(RT ~ PartID + CueType,
-            data = Trialdata,
-            FUN = mean)
-T1mean[["PrepTarget"]] <- aggregate(RT ~ PartID + CueType + Target,
-                                 data = Trialdata,
-                                 FUN = mean)
-T1mean[["Distraction"]] <- aggregate(RT ~ PartID + Distractor,
-            data = Trialdata,
-            FUN = mean)
-T1mean[["DistractionTarget"]] <-
-  aggregate(RT ~ PartID + Distractor + Target,
-            data = Trialdata,
-            FUN = mean)
-T1mean[["Condition"]] <- aggregate(RT ~ PartID + Condition,
-            data = Trialdata,
-            FUN = mean)
-T1mean[["ConditionModality"]] <- aggregate(RT ~ PartID + Condition + Target,
-            data = Trialdata,
-            FUN = mean)
-T1mean[["ConditionPreparation"]] <- aggregate(RT ~ PartID + Condition + CueType,
-            data = Trialdata,
-            FUN = mean)
-T1mean[["ConditionDistraction"]] <- aggregate(RT ~ PartID + Condition + Distractor,
-            data = Trialdata,
-            FUN = mean)
+## Create formatted summary table of Behavioural results to support plots and analysis
+VOI <- c("Target","CueType","Distractor")
+RT_means <- list()
+Error_means <- list()
 
-# Number of Trials for Error calcs
-NTrials <-
-  aggregate(TrialNum ~ PartID + Condition + CueType + Target + Distractor + Accuracy,
-            data = Trialdata,
-            FUN = length)
-names(NTrials)[length(NTrials)] <- "NTrials"
-# Create grouping variable to help calc percentages
-NTrials$levels <- interaction(NTrials$PartID,NTrials$Condition,NTrials$CueType,NTrials$Target,NTrials$Distractor,sep = ".")
+for (i in VOI){
+# Correct RT
+RT_means[["Correct"]][[i]] <- Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, get(i), Condition) %>%
+    dplyr::summarise(subjRT = mean(RT, na.rm = T)) %>%
+    dplyr::group_by(`get(i)`, Condition) %>% 
+    dplyr::summarise(RT = mean(subjRT, na.rm = T),
+                     SD = sd(subjRT, na.rm = T)) %>% 
+  dplyr::ungroup()
+names(RT_means[["Correct"]][[i]]) <- c("Variable", "Condition","RT","SD")
 
-ErrorRates <- list()
-for (i in unique(NTrials$levels)) {
-  dummy <- ((NTrials$NTrials[NTrials$levels == i &
-                            NTrials$Accuracy == "Error"] / sum(NTrials$NTrials[NTrials$levels == i])) * 100)
+# Error RT
+RT_means[["Error"]][[i]] <- Trialdata %>%
+    dplyr::filter(Accuracy == "Error") %>%
+    dplyr::group_by(PartID, get(i), Condition) %>%
+    dplyr::summarise(subjRT = mean(RT, na.rm = T)) %>%
+    dplyr::group_by(`get(i)`, Condition) %>% 
+    dplyr::summarise(RT = mean(subjRT, na.rm = T),
+                     SD = sd(subjRT, na.rm = T)) %>% 
+  dplyr::ungroup()
+names(RT_means[["Error"]][[i]]) <- c("Variable", "Condition","Error RT","SD")
 
-  ErrorRates[["ErrorRates"]][[i]] <-
-    unlist(ifelse(length(dummy) == 0, NA, dummy))
+# Error Rates
+Error_means[["Error"]][[i]] <- Trialdata %>% 
+  dplyr::group_by(PartID, get(i), Accuracy, Condition) %>% 
+  dplyr::tally() %>% 
+  dplyr::group_by(PartID, `get(i)`, Condition) %>% 
+  dplyr::mutate(total = sum(n)) %>% 
+  dplyr::mutate(perc = (n /total) * 100) %>% 
+  dplyr::select(-n, -total) %>% 
+  dplyr::filter(Accuracy =="Error") %>% 
+  dplyr::group_by(`get(i)`,Condition) %>% 
+  dplyr::summarise(Errors = mean(perc, na.rm=T),
+                   SD = sd(perc,na.rm = T)) %>% 
+  dplyr::ungroup()
+names(Error_means[["Error"]][[i]]) <- c("Variable", "Condition","Errors (%)","SD")
 
-  dummy2 <- (NTrials$NTrials[NTrials$levels == i &
-                            NTrials$Accuracy == "Miss"] / sum(NTrials$NTrials[NTrials$levels == i]) * 100)
+# Miss Rates
+Error_means[["Miss"]][[i]] <- Trialdata %>% 
+  dplyr::group_by(PartID, get(i), Accuracy, Condition) %>% 
+  dplyr::tally() %>% 
+  dplyr::group_by(PartID, `get(i)`, Condition) %>% 
+  dplyr::mutate(total = sum(n)) %>% 
+  dplyr::mutate(perc = (n /total) * 100) %>% 
+  dplyr::select(-n, -total) %>% 
+  dplyr::filter(Accuracy =="Miss") %>% 
+  dplyr::group_by(`get(i)`,Condition) %>% 
+  dplyr::summarise(Errors = mean(perc, na.rm=T),
+                   SD = sd(perc,na.rm = T)) %>% 
+  dplyr::ungroup()
+names(Error_means[["Miss"]][[i]]) <- c("Variable", "Condition","Omissions (%)","SD")
 
-  ErrorRates[["MissRates"]][[i]] <-
-    unlist(ifelse(length(dummy2) == 0, NA, dummy2))
 }
-rm(dummy,dummy2)
 
-Errorsdata <- data.frame(ErrorRates)
-Errorsdata$levels <- rownames(Errorsdata)
-foo <- do.call(rbind,strsplit(Errorsdata$levels,split = "[.]"))
-colnames(foo) <- names(T1mean$All)[1:ncol(foo)]
-Errorsdata <- cbind(foo,Errorsdata) %>% select(-levels)
+# Format Table 1 - other option is to group RT, seperate to Errors/Omissions (table currently too big imo)
+Tab1_RT <- dplyr::bind_rows(RT_means$Correct,
+                      .id = "Effect")
+Tab1_RT <- cbind(RT_means$Correct[RT_means$Correct])
+Tab1_RTerr <- dplyr::bind_rows(RT_means$Error,
+                      .id = "Effect")
+Tab1_Err <- dplyr::bind_rows(Error_means$Error,
+                      .id = "Effect")
+Tab1_Miss <- dplyr::bind_rows(Error_means$Miss,
+                      .id = "Effect")
 
-T1err <- list()
-T1err[["Modality"]] <- 
-  aggregate(ErrorRates ~ PartID + Target,
-            data = Errorsdata,
-            FUN = mean)
-T1err[["Preparation"]] <-
-  aggregate(ErrorRates ~ PartID + CueType, 
-            data = Errorsdata, 
-            FUN = mean)
-T1err[["PrepTarget"]] <- aggregate(ErrorRates ~ PartID + CueType + Target,
-                                 data = Errorsdata,
-                                 FUN = mean)
-T1err[["Distraction"]] <-
-  aggregate(ErrorRates ~ PartID + Distractor,
-            data = Errorsdata,
-            FUN = mean)
-T1err[["DistractionTarget"]] <-
-  aggregate(ErrorRates ~ PartID + Distractor + Target,
-            data = Errorsdata,
-            FUN = mean)
-T1err[["Condition"]] <- 
-  aggregate(ErrorRates ~ PartID + Condition,
-            data = Errorsdata,
-            FUN = mean)
+np_Tab1 <- cbind(Tab1_RT[Tab1_RT$Condition=="No Pain",],
+                 Tab1_RTerr[Tab1_RTerr$Condition=="No Pain",][c("Error RT", "SD")],
+                 Tab1_Err[Tab1_Err$Condition=="No Pain",][c("Errors (%)", "SD")],
+                 Tab1_Miss[Tab1_Miss$Condition=="No Pain",][c("Omissions (%)", "SD")]
+)
+np_Tab1$Condition <- NULL
+np_Tab1$Effect <- NULL
 
-T1omm <- list()
-T1omm[["Modality"]] <- 
-  aggregate(MissRates ~ PartID + Target,
-            data = Errorsdata,
-            FUN = mean)
-T1omm[["Preparation"]] <-
-  aggregate(MissRates ~ PartID + CueType, 
-            data = Errorsdata, 
-            FUN = mean)
-T1omm[["Distraction"]] <-
-  aggregate(MissRates ~ PartID + Distractor,
-            data = Errorsdata,
-            FUN = mean)
-T1omm[["DistractionTarget"]] <-
-  aggregate(MissRates ~ PartID + Distractor + Target,
-            data = Errorsdata,
-            FUN = mean)
-T1omm[["PrepTarget"]] <- aggregate(MissRates ~ PartID + CueType + Target,
-                                 data = Errorsdata,
-                                 FUN = mean)
-T1omm[["Condition"]] <- 
-  aggregate(MissRates ~ PartID + Condition,
-            data = Errorsdata,
-            FUN = mean)
+p_Tab1 <- cbind(Tab1_RT[Tab1_RT$Condition=="Pain",],
+                 Tab1_RTerr[Tab1_RTerr$Condition=="Pain",][c("Error RT", "SD")],
+                 Tab1_Err[Tab1_Err$Condition=="Pain",][c("Errors (%)", "SD")],
+                 Tab1_Miss[Tab1_Miss$Condition=="Pain",][c("Omissions (%)", "SD")]
+)
+p_Tab1$Condition <- NULL
+p_Tab1$Effect <- NULL
+
+Table1 <- cbind(np_Tab1,p_Tab1)
+names(Table1) <-
+  c(
+  "",
+  "RT",
+  "SD",
+  "Error RT",
+  "SD",
+  "Errors (%)",
+  "SD",
+  "Omissions (%)",
+  "SD",
+  "Variable",
+  "RT",
+  "SD",
+  "Error RT",
+  "SD",
+  "Errors (%)",
+  "SD",
+  "Omissions (%)",
+  "SD"
+  )
+Table1$Variable <- NULL
+
+# Paste the SD with the RT in brackets? - round to 2 digits
+
+# Print Table 1
+# Column headers for Condition
+# Row Groupings for Modality, Cue Type, Distractor
+kable(Table1, caption = "Table 1. Behavoural Summary Stats",digits = 2) %>%
+  kable_styling("striped", full_width = F) %>%
+ add_header_above(c(" " = 1, "No Pain" = 8, "Pain" = 8)) %>% 
+  pack_rows("Modality", 1, 2) %>%
+  pack_rows("Cue Type", 3, 5) %>% 
+  pack_rows("Distractor",6, 7)
+
 ```
@@
 
-## 3.1. Behavioural Results Models
+## 3.1. Behavioural Models
 ```{r RT Tests, eval=FALSE, include=FALSE}
@@
 
-# ## Linear Models take longer than straight ANOVAs?
-# RTBayeslm_all <-
-#   BayesFactor::anovaBF(
-#     RT ~ Target * CueType * Condition + PartID,
-#     data = Trialdata[!is.na(Trialdata$RT),],
-#     whichRandom = "PartID",
-#     progress = T,
-#     iterations = 10
-# )
-# 
-# RTBayeslm_NullComparison <- head(RTBayeslm_all)/max(RTBayeslm_all)
-# ## See differences between most supported model
-# plot(RTBayeslm_NullComparison)
+## Linear Models take longer than straight ANOVAs?
+system.time(
+RTBayes_all <-
+  BayesFactor::anovaBF(
+    RT ~ Target * CueType * Condition + PartID,
+    data = Trialdata[!is.na(Trialdata$RT),],
+    whichRandom = "PartID",
+    progress = T,
+    iterations = 1000,
+    whichModels = "top"
+    ))
+
+system.time(
+RTBayes <-
+  BayesFactor::anovaBF(
+    RT ~ Target * CueType + PartID,
+    data = Trialdata[!is.na(Trialdata$RT),],
+    whichRandom = "PartID",
+    progress = T,
+    iterations = 10000,
+    whichModels = "top"
+
+    ))
+
+# 10 =    user  system elapsed 
+#       115.38    0.21  119.02
+
+# 5 =    user  system elapsed 
+#      115.34    0.32  116.86
+
+# Turn into bf_ format
+bf_model <- bayesfactor_models(RTBayes_all)
+bayestestR::bayesfactor_inclusion(bf_model,match_models = F)
+
+bayestestR::bf_inclusion(RTBayes_all)
+
+RTBayeslm_NullComparison <- head(RTBayeslm_all)/max(RTBayeslm_all)
+## See differences between most supported model
+plot(RTBayeslm_NullComparison)
 ```

### 2020-07-16 Functions/ErrRates.R

@@ -1,4 +1,5 @@
 ErrRates <- function(list, sublist, sublist_levels,subj) {
+  
   ErrorRates <- list()
   OmmRates   <- list()
   
@@ -11,6 +12,7 @@ ErrRates <- function(list, sublist, sublist_levels,subj) {
         (subjdummy$n[subjdummy[[sublist]] == x &
                        subjdummy$Accuracy == "Miss"] / sum(subjdummy$n[subjdummy[[sublist]] == x])) * 100)
     names(OmmRates[[i]]) <- sublist_levels
+    OmmRates[[i]] <- ifelse(length(unlist(OmmRates[[i]]))==0,NA,OmmRates[[i]])
   
     ## Do the same for errors
     ErrorRates[[i]] <-
@@ -18,12 +20,13 @@ ErrRates <- function(list, sublist, sublist_levels,subj) {
         (subjdummy$n[subjdummy[[sublist]] == x &
                        subjdummy$Accuracy == "Error"] / sum(subjdummy$n[subjdummy[[sublist]] == x])) * 100)
     names(ErrorRates[[i]]) <- sublist_levels
+    ErrorRates[[i]] <- ifelse(length(unlist(ErrorRates[[i]]))==0,NA,ErrorRates[[i]])
+    
     
   }
   names(OmmRates) <- subj
   names(ErrorRates) <- subj
   ## Transform into data frames
-  
   
   OmmRates.data <- data.frame(do.call(rbind,OmmRates))
   ErrorRates.data <- data.frame(do.call(rbind,ErrorRates))

### 2020-07-16 Functions/RT_RainPlots.R

@@ -1,0 +1,97 @@
+RT_RainPlot <- function(data,
+                        xval,
+                        groupval,
+                        w = 16,
+                        h = 9) {
+  # width and height variables for saved plots
+  w = w
+  h = h
+  
+  ## Take full data frame and reduce down into a list of smaller data frames with the same names.
+  
+  #e.g.,
+  Plotdata <- list()
+  
+  Plotdata[[paste(xval, groupval, sep = "")]] <- data %>%
+    dplyr::filter(Accuracy != "Miss") %>% # This is necessary across all RT data - Hard coded!
+    dplyr::group_by(PartID, get(xval), get(groupval)) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T))
+  
+  names(Plotdata[[paste(xval, groupval, sep = "")]]) <-
+    c("PartID", "xval", "groupval", "RT")
+  
+  wse <- list()
+  wse[[paste(xval, groupval, sep = "")]] <- Rmisc::summarySEwithin(
+    Plotdata[[paste(xval, groupval, sep = "")]],
+    measurevar = "RT",
+    withinvars = c("xval", "groupval"),
+    idvar = "PartID",
+    na.rm = T,
+    conf.interval = .95
+  )
+  
+  ## Make and save plot
+  ggplot(Plotdata[[paste(xval, groupval, sep = "")]], aes(x = xval, y = RT, fill = groupval)) +
+    geom_flat_violin(
+      aes(fill = groupval),
+      position = position_nudge(x = .1, y = 0),
+      adjust = 1.5,
+      trim = FALSE,
+      alpha = .5,
+      colour = NA
+    ) +
+    geom_point(
+      aes(
+        x = as.numeric(xval) - .15,
+        y = RT,
+        colour = groupval
+      ),
+      position = position_jitter(width = .05),
+      size = 1.5,
+      shape = 20
+    ) +
+    geom_boxplot(
+      aes(x = xval, y = RT, fill = groupval),
+      outlier.shape = NA,
+      alpha = .5,
+      width = .1,
+      colour = "black"
+    ) +
+    geom_point(
+      data = wse[[paste(xval, groupval, sep = "")]],
+      aes(
+        x = as.numeric(xval) +-.15,
+        y = RT,
+        group = groupval,
+        colour = groupval
+      ),
+      shape = 18,
+      size = 3
+    ) +
+    geom_errorbar(
+      data = wse[[paste(xval, groupval, sep = "")]],
+      aes(
[…]

### 2020-08-28 ManuscriptMarkdown.Rmd
Adjusted code to investigate illogical RT

@@
               "rmarkdown","data.table","devtools",
-              "cowplot","dplyr","readr") # Slew of packages used here.
+              "cowplot","readr") # Slew of packages used here.
 
@@
 
+# Seed setting for Bayes
+set.seed(930129)
+
 # Knitting options
@@
 # As per the following document. Only CLP106 -> CLP 149 are useable
-PainCodes <- read.csv("EEGIdentity.csv")
+PainCodes <- read.csv("PainRatings.csv")
 PainCodes$Subjidx <- paste("CLP",PainCodes$Subjidx,sep = "")
 
-Subjidx <- dir(path = "Data/RejectData/",
+Subjidx <- dir(path = "Data/",
                pattern = "CLP*")
-# Remove CLP116_2 until we know what that's about.
-Subjidx <- Subjidx[Subjidx != "CLP116_2"]
-
-# Seperate into those with pain data and those without
-pain_Subjidx <- Subjidx[unlist(
-  lapply(Subjidx, function(px)
-    file.exists(
-      paste("Data/RejectData/", px, "/", px, "_p_BadChannels.txt",sep = "")
-    )))]
-
-# Reduce particpants down to finalised numbers
-PainCodes <- PainCodes[PainCodes$Subjidx %in% Subjidx,]
+
+# Remove CLP116 - Didn't finish
+Subjidx <- Subjidx[Subjidx != "CLP116"]
+# Remove CLP1107 - Odd Trigger codes 
+Subjidx <- Subjidx[Subjidx != "CLP107"]
+# Remove CLP130 - Odd trigger codes
+Subjidx <- Subjidx[Subjidx != "CLP130"]
 
@@
 if(!file.exists("Output/Trial_list.RData")){
-Trial.list <- list()
+Trial.list <- list(np = list(),
+                   p = list())
 ## Extract Trial.list
 for(px in seq_along(Subjidx)){
-  Trial.list[["np"]][[px]] <- ExtractTrialData(PartID = Subjidx[px],COND = "np")
+  Trial.list[["np"]][[px]] <- ExtractTrialData(PartID = Subjidx[px],
+                                               COND = "np",
+                                               dataloc = "Data/")
 
@@
 names(Trial.list[["np"]]) <- Subjidx
-
-# N.B - CLP116 is missing pain data
-Subjidx_p <- Subjidx[-16]
-for (px in seq_along(Subjidx)) {
-  if (file.exists(paste(
-    "../Data/",
-    Subjidx[px],
-    "/Behaviour/",
-    paste(Subjidx[px], "p", sep = "_"),
-    "_EventCodes.mat",
-    sep = ""
-  ))) {
-    Trial.list[["p"]][[px]] <-
-      ExtractTrialData(PartID = Subjidx[px], COND = "p")
-  }
-  else {
-    Trial.list[["p"]][[px]] <- NA
-  }
+Trial.list[["np"]] <- Trial.list[["np"]][!is.na(Trial.list[["np"]])]
+
+for(px in seq_along(Subjidx)){
+  Trial.list[["p"]][[px]] <- ExtractTrialData(PartID = Subjidx[px],
+                                               COND = "p",
+                                               dataloc = "Data/")
+
 }
 names(Trial.list[["p"]]) <- Subjidx
-
-## Remove CLP116 pain data
-Trial.list[["p"]][is.na(Trial.list[["p"]])] <- NULL
-
-save(Trial.list,file = "Output/Trial_list.RData")
-
-Trialdata <- rbind(data.table::rbindlist(Trial.list$np),
-                 data.table::rbindlist(Trial.list$p))
-write.csv(Trialdata,file = "Output/TrialData.csv",
+Trial.list[["p"]] <- Trial.list[["p"]][!is.na(Trial.list[["p"]])]
+
+save(Trial.list, file = "Output/Trial_list.RData")
+Trialdata <- rbind(data.table::rbindlist(Trial.list[["np"]]),
+                   data.table::rbindlist(Trial.list[["p"]]))
+
+# Mark participants who recieved pain:
+Trialdata$Rec_pain <- 0
+Trialdata$Rec_pain[Trialdata$PartID %in% PainCodes$Subjidx] <- 1
+
+write.csv(Trialdata, file = "Output/TrialData.csv",
           row.names = F)
@@
 Trialdata <- read.csv("Output/TrialData.csv")
+
+# Subset Participants from Trialdata
 Trialdata <- Trialdata[Trialdata$PartID %in% Subjidx,]
+Trialdata$PartID <- factor(Trialdata$PartID)
+rownames(Trialdata) <- seq(from = 1, to = nrow(Trialdata),by=1)
+```
+
+``` {r Sanity Checks}
+
+#### TODO Fix this section up. Make it presentable ####
+### We want to:
+# Find incorrect trigger codes, i.e., short/long CTI/ITIs and remove
+# Cut short RT ~<150ms
+# Cut long RT >1000ms?
+
+hist(Trialdata$RT, breaks = 100)
+hist(Trialdata$RT[Trialdata$RT<250], breaks = 100)
+
+table(Trialdata$PartID[Trialdata$RT<150])
+table(Trialdata$Condition[Trialdata$RT<150]) # Slight condition difference
+table(Trialdata$Accuracy[Trialdata$RT<150])
+
+# Long responses
+table(Trialdata$PartID[Trialdata$RT>800])
+table(Trialdata$Condition[Trialdata$RT>800])
+table(Trialdata$Accuracy[Trialdata$RT>800])
 
 ## check CTI and ITI values:
-hist(Trialdata$CTI)
-hist(Trialdata$ITI)
-table(Trialdata$PartID[Trialdata$ITI>4000]) # CLP114 and CLP124 might need a look into for long ITIs
+hist(Trialdata$CTI, breaks = 100)
+hist(Trialdata$CTI[Trialdata$CTI<700], breaks = 100)
+table(Trialdata$PartID[Trialdata$CTI<600]) # One short CIT. - Error
+ShortCTI <- list(,
+                 )
+
+# Remove it
+Trialdata <- Trialdata[-c(10271,12882),]
+
+hist(Trialdata$CTI[Trialdata$CTI>800], breaks = 100)
+table(Trialdata$PartID[Trialdata$CTI>850]) # One long CTI - Miss
+
+median(Trialdata$CTI, na.rm = T)
+min(Trialdata$CTI[Trialdata$CTI>500], na.rm = T)
+
+hist(Trialdata$ITI, breaks = 100)
+table(Trialdata$ITI)
+hist(Trialdata$ITI[Trialdata$ITI>2500], breaks = 100)
+hist(Trialdata$ITI[Trialdata$ITI<2000], breaks = 100)
+
+table(Trialdata$PartID[Trialdata$ITI>3000])
+table(Trialdata$PartID[Trialdata$ITI<1850])
+
+Trialdata <- Trialdata[-c(4823),]
+
+summary(Trialdata$ITI[Trialdata$ITI<3000])
+
+Trialdata$RT[Trialdata$RT<150] <- NA
+
+## Re-level the CueType data into cued and ambiguous
+levels(Trialdata$CueType) <- list("Ambiguous" = "Ambiguous", "Cued" = c("Auditory","Visual"))
+
+## Plot pain response
+painplots <- PainCodes %>% dplyr::filter(AveragePainRating >= 20) %>% dplyr::select(Subjidx,Start,contains("Break")) %>% 
+  tidyr::gather(Time,Pain,Start:Break5)
+painplots$Time <- factor(painplots$Time,levels = c("Start", "Break1", "Break2", "Break3", "Break4", "Break5"))
+
+painplots_summ <- Rmisc::summarySEwithin(
+  painplots,
+  measurevar = "Pain",
+  withinvars = "Time",
+  idvar = "Subjidx",
+  na.rm = T,
+  conf.interval = .95
+)
+
+ggplot(data = painplots,aes(x = Time,y = Pain,group = Subjidx,colour = Subjidx)) +
+  geom_point() + geom_line() +
+    stat_summary(aes(y = Pain,group=1), fun=mean, colour="red", lwd = 1, geom="line",group=1) +
+      # stat_summary(aes(y = Pain,group=1),fun.data = mean_se,colour="red", lwd = 1,
+      #            geom = "errorbar")+
+  theme_classic() +
+  theme(legend.position = 'none') +
+  labs(x = "Time Points",
+       y = "Pain Rating (%)") + 
+    scale_colour_grey()
 
@@
 Summdata <- MethodsList(Trialdata) # Can ignore warnings - RE: mean RT for miss trials/SD for 2 trials total
+# Mark participants who recieved pain:
+Summdata$Rec_pain <- 0
+Summdata$Rec_pain[Summdata$PartID %in% PainCodes$Subjidx] <- 1
 ```
@@
 Trigger codes did not specify exactly*].
-The cue to target interval (CIT) jittered between `r round(min(Trialdata$CTI,na.rm=T),0)`-`r round(max(Trialdata$CTI,na.rm=T),0)` in steps of **XXX** (*Values for this change with participants.
+The cue to target interval (CIT) jittered between `r min(Trialdata$CTI[Trialdata$CTI>300],na.rm = T)`-`r max(Trialdata$CTI[Trialdata$CTI<1400],na.rm = T)` in steps of **XXX** (*Values for this change with participants.
 Some have maxes of ~800ms and min of ~700ms.
-Others (N = 3) have max ~1500 and min ~1400* **I beleive I have fixed this with removal of some px**).
-Each trial lasted approximately `r round(mean(Trialdata %>% group_by(PartID) %>% summarise(meanITI = mean(ITI,na.rm=T)) %>% .$meanITI),0)`, with a jitter of **XXX**.
+Others have max ~1500 and min ~200*).
+Each trial lasted an average of `r round(mean(Trialdata %>% group_by(PartID) %>% summarise(meanITI = mean(ITI,na.rm=T)) %>% .$meanITI),0)`ms.
 
@@
 Peripheral recordings of galvantic skin conductance, heart rate, and respiration were taken.
+
+### 2.2.3. Heat Pain
+  Pain was delivered
 
@@
                                               read.table(
-                                                paste("Data/RejectData/",
-                                                      px, "/",
+                                                paste("Data/",
+                                                      px, "/Stats/",
                                                       px,
@@
 
-EEGPreProc[["BadChan"]][["p"]] <- lapply(pain_Subjidx,
+EEGPreProc[["BadChan"]][["p"]] <- lapply(Subjidx,
                                          function(px)
@@
                                              read.table(
-                                               paste("Data/RejectData/",
-                                                     px, "/",
+                                               paste("Data/",
+                                                      px, "/Stats/",
                                                       px,
@@
 
-names(EEGPreProc[["BadChan"]][["p"]]) <- pain_Subjidx
+names(EEGPreProc[["BadChan"]][["p"]]) <- Subjidx
 
@@
 
-EEGPreProc[["RejComp"]][["p"]] <- lapply(pain_Subjidx,
+EEGPreProc[["RejComp"]][["p"]] <- lapply(Subjidx,
                                          function(px)
@@
                                              read.table(
-                                               paste("Data/RejectData/",
-                                                     px, "/",
+                                                paste("Data/",
+                                                      px, "/Stats/",
                                                       px,
@@
 
-names(EEGPreProc[["RejComp"]][["p"]]) <- pain_Subjidx
+names(EEGPreProc[["RejComp"]][["p"]]) <- Subjidx
 
@@
 
-## Summarise number of removed trials
-EEGPreProc[["RejTrial"]][["np"]][["Visual"]] <- lapply(Subjidx,
-                                                       function(px)
-                                                         read.table(
-                                                           paste(
-                                                             "Data/RejectData/",
-                                                             px,
-                                                             "/",
-                                                             px,
-                                                             "_np_RF_Proc_RejTrials.txt",
-                                                             sep = ""
-                                                           ),
-                                                           row.names = NULL,
-                                                           quote = "\"",
-                                                           comment.char = ""
-                                                         )[[1, 1]])
-
-names(EEGPreProc[["RejTrial"]][["np"]][["Visual"]]) <- Subjidx
-
-EEGPreProc[["RejTrial"]][["np"]][["Auditory"]] <- lapply(Subjidx,
-                                                       function(px)
-                                                         read.table(
-                                                           paste(
-                                                             "Data/RejectData/",
-                                                             px,
-                                                             "/",
-                                                             px,
-                                                             "_np_RF_Proc_RejTrials.txt",
-                                                             sep = ""
-                                                           ),
-                                                           row.names = NULL,
-                                                           quote = "\"",
-                                                           comment.char = ""
-                                                         )[[2, 1]])
-
-names(EEGPreProc[["RejTrial"]][["np"]][["Auditory"]]) <- Subjidx
-
-EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]] <- lapply(Subjidx,
-                                                       function(px)
-                                                         read.table(
-                                                           paste(
-                                                             "Data/RejectData/",
-                                                             px,
-                                                             "/",
-                                                             px,
-                                                             "_np_RF_Proc_RejTrials.txt",
-                                                             sep = ""
-                                                           ),
-                                                           row.names = NULL,
-                                                           quote = "\"",
-                                                           comment.char = ""
-                                                         )[[3, 1]])
-
-names(EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]]) <- Subjidx
-
-EEGPreProc[["RejTrial"]][["p"]][["Visual"]] <- lapply(pain_Subjidx,
-                                                       function(px)
-                                                         read.table(
-                                                           paste(
-                                                             "Data/RejectData/",
-                                                             px,
-                                                             "/",
-                                                             px,
-                                                             "_p_RF_Proc_RejTrials.txt",
-                                                             sep = ""
-                                                           ),
-                                                           row.names = NULL,
-                                                           quote = "\"",
-                                                           comment.char = ""
-                                                         )[[1, 1]])
-
-names(EEGPreProc[["RejTrial"]][["p"]][["Visual"]]) <- pain_Subjidx
-
-EEGPreProc[["RejTrial"]][["p"]][["Auditory"]] <- lapply(pain_Subjidx,
-                                                       function(px)
-                                                         read.table(
-                                                           paste(
-                                                             "Data/RejectData/",
-                                                             px,
-                                                             "/",
-                                                             px,
-                                                             "_p_RF_Proc_RejTrials.txt",
-                                                             sep = ""
-                                                           ),
-                                                           row.names = NULL,
-                                                           quote = "\"",
-                                                           comment.char = ""
-                                                         )[[2, 1]])
-
-names(EEGPreProc[["RejTrial"]][["p"]][["Auditory"]]) <- pain_Subjidx
-
-EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]] <- lapply(pain_Subjidx,
-                                                       function(px)
-                                                         read.table(
-                                                           paste(
-                                                             "Data/RejectData/",
-                                                             px,
-                                                             "/",
-                                                             px,
-                                                             "_p_RF_Proc_RejTrials.txt",
-                                                             sep = ""
-                                                           ),
-                                                           row.names = NULL,
-                                                           quote = "\"",
-                                                           comment.char = ""
-                                                         )[[3, 1]])
-
-names(EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]]) <- pain_Subjidx
-
-# Both conditions together
-EEGPreProc[["RejTrial"]][["Both"]][["Visual"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Visual"]][Subjidx],                                                       EEGPreProc[["RejTrial"]][["p"]][["Visual"]][Subjidx]), Subjidx)
-
-EEGPreProc[["RejTrial"]][["Both"]][["Auditory"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Auditory"]][Subjidx], EEGPreProc[["RejTrial"]][["p"]][["Auditory"]][Subjidx]), Subjidx)
-
-EEGPreProc[["RejTrial"]][["Both"]][["Ambiguous"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]][Subjidx], EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]][Subjidx]), Subjidx)
-
-# Both conditions averaged
-EEGPreProc[["RejTrial"]][["Average"]][["Visual"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Visual"]][[x]]))
-
-EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Auditory"]][[x]]))
-
-EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Ambiguous"]][[x]]))
-
-## Total Trials Removed
-EEGPreProc[["RejTrial"]][["Total"]] <- lapply(seq_along(Subjidx),
-                                              function(x)
-                                              sum(EEGPreProc[["RejTrial"]][["Average"]][["Visual"]][[x]],
-                                              EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]][[x]],
-                                              EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]][[x]]))
-
-Perc_TrialsRemoved <- data.frame(Vis = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Visual"]])/120),
-                            Aud = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]])/120),
-                            Amb = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]])/60))
-## Compare Cue Types on the percentage of removed trials
-# format data
-TrialsRemoved_test <- reshape2::melt(Perc_TrialsRemoved)
-# Freq test
-TR_ANOVA <- aov(value ~ variable, data = TrialsRemoved_test)
-# Bayes test
-BF_TR_ANOVA <- BayesFactor::anovaBF(value ~ variable, data = TrialsRemoved_test)
-```
+## Summarise number of removed trials - Removed from current pipeline
+# EEGPreProc[["RejTrial"]][["np"]][["Visual"]] <- lapply(Subjidx,
+#                                                        function(px)
+#                                                          read.table(
+#                                                            paste(
+#                                                              "Data/RejectData/",
+#                                                              px,
+#                                                              "/",
+#                                                              px,
+#                                                              "_np_RF_Proc_RejTrials.txt",
+#                                                              sep = ""
+#                                                            ),
+#                                                            row.names = NULL,
+#                                                            quote = "\"",
+#                                                            comment.char = ""
+#                                                          )[[1, 1]])
+# 
+# names(EEGPreProc[["RejTrial"]][["np"]][["Visual"]]) <- Subjidx
+# 
+# EEGPreProc[["RejTrial"]][["np"]][["Auditory"]] <- lapply(Subjidx,
+#                                                        function(px)
+#                                                          read.table(
+#                                                            paste(
+#                                                              "Data/RejectData/",
+#                                                              px,
+#                                                              "/",
+#                                                              px,
+#                                                              "_np_RF_Proc_RejTrials.txt",
+#                                                              sep = ""
+#                                                            ),
+#                                                            row.names = NULL,
+#                                                            quote = "\"",
+#                                                            comment.char = ""
+#                                                          )[[2, 1]])
+# 
+# names(EEGPreProc[["RejTrial"]][["np"]][["Auditory"]]) <- Subjidx
+# 
+# EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]] <- lapply(Subjidx,
+#                                                        function(px)
+#                                                          read.table(
+#                                                            paste(
+#                                                              "Data/RejectData/",
+#                                                              px,
+#                                                              "/",
+#                                                              px,
+#                                                              "_np_RF_Proc_RejTrials.txt",
+#                                                              sep = ""
+#                                                            ),
+#                                                            row.names = NULL,
+#                                                            quote = "\"",
+#                                                            comment.char = ""
+#                                                          )[[3, 1]])
+# 
+# names(EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]]) <- Subjidx
+# 
+# 
+# EEGPreProc[["RejTrial"]][["p"]][["Visual"]] <- lapply(pain_Subjidx,
+#                                                        function(px)
+#                                                          read.table(
+#                                                            paste(
+#                                                              "Data/RejectData/",
+#                                                              px,
+#                                                              "/",
+#                                                              px,
+#                                                              "_p_RF_Proc_RejTrials.txt",
+#                                                              sep = ""
+#                                                            ),
+#                                                            row.names = NULL,
+#                                                            quote = "\"",
+#                                                            comment.char = ""
+#                                                          )[[1, 1]])
+# 
+# names(EEGPreProc[["RejTrial"]][["p"]][["Visual"]]) <- pain_Subjidx
+# 
+# EEGPreProc[["RejTrial"]][["p"]][["Auditory"]] <- lapply(pain_Subjidx,
+#                                                        function(px)
+#                                                          read.table(
+#                                                            paste(
+#                                                              "Data/RejectData/",
+#                                                              px,
+#                                                              "/",
+#                                                              px,
+#                                                              "_p_RF_Proc_RejTrials.txt",
+#                                                              sep = ""
+#                                                            ),
+#                                                            row.names = NULL,
+#                                                            quote = "\"",
+#                                                            comment.char = ""
+#                                                          )[[2, 1]])
+# 
+# names(EEGPreProc[["RejTrial"]][["p"]][["Auditory"]]) <- pain_Subjidx
+# 
+# EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]] <- lapply(pain_Subjidx,
+#                                                        function(px)
+#                                                          read.table(
+#                                                            paste(
+#                                                              "Data/RejectData/",
+#                                                              px,
+#                                                              "/",
+#                                                              px,
+#                                                              "_p_RF_Proc_RejTrials.txt",
+#                                                              sep = ""
+#                                                            ),
+#                                                            row.names = NULL,
+#                                                            quote = "\"",
+#                                                            comment.char = ""
+#                                                          )[[3, 1]])
+# 
+# names(EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]]) <- pain_Subjidx
+# 
+# # Both conditions together
+# EEGPreProc[["RejTrial"]][["Both"]][["Visual"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Visual"]][Subjidx],                                                       EEGPreProc[["RejTrial"]][["p"]][["Visual"]][Subjidx]), Subjidx)
+# 
+# EEGPreProc[["RejTrial"]][["Both"]][["Auditory"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Auditory"]][Subjidx], EEGPreProc[["RejTrial"]][["p"]][["Auditory"]][Subjidx]), Subjidx)
+# 
+# EEGPreProc[["RejTrial"]][["Both"]][["Ambiguous"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]][Subjidx], EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]][Subjidx]), Subjidx)
+# 
+# # Both conditions averaged
+# EEGPreProc[["RejTrial"]][["Average"]][["Visual"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Visual"]][[x]]))
+# 
+# EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Auditory"]][[x]]))
+# 
+# EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Ambiguous"]][[x]]))
+# 
+# ## Total Trials Removed
+# EEGPreProc[["RejTrial"]][["Total"]] <- lapply(seq_along(Subjidx),
+#                                               function(x)
+#                                               sum(EEGPreProc[["RejTrial"]][["Average"]][["Visual"]][[x]],
+#                                               EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]][[x]],
+#                                               EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]][[x]]))
+# 
+# Perc_TrialsRemoved <- data.frame(Vis = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Visual"]])/120),
+#                             Aud = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]])/120),
+#                             Amb = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]])/60))
+# ## Compare Cue Types on the percentage of removed trials
+# # format data
+# TrialsRemoved_test <- reshape2::melt(Perc_TrialsRemoved)
+# # Freq test
+# TR_ANOVA <- aov(value ~ variable, data = TrialsRemoved_test)
+# # Bayes test
+# BF_TR_ANOVA <- BayesFactor::anovaBF(value ~ variable, data = TrialsRemoved_test)
+```
+
   An outline of the EEG pre-processing undertaken here is presented in Figure *X*.
@@
 Channels were then interpolated using *pop_interp* and data epoched 1.5s before the cue to 2.5s post-cue, for each cue seperately.
-EEGLABs extreme epoch noise detection using EEGLab's threshold & joint probability procedures was undertaken with the cut-off for amplitude set at 100uV **put in other stuff heree**.
-An average of `r round(mean(unlist(EEGPreProc$RejTrial$Average)),2)` +/- `r round(sd(unlist(EEGPreProc$RejTrial$Average)),2)` trials were removed using this procedure for each participant.
 Lastly, data were current source density transformed useing Fieldtrips *ft_scalpcurrentdensity* using the spline method.
-  An average of `r round(mean(unlist(EEGPreProc[["RejTrial"]][["Total"]])),2)` +/- `r round(sd(unlist(EEGPreProc[["RejTrial"]][["Total"]])),2)` trials were removed for each participant.
+  <!-- An average of `r round(mean(unlist(EEGPreProc[["RejTrial"]][["Total"]])),2)` +/- `r round(sd(unlist(EEGPreProc[["RejTrial"]][["Total"]])),2)` trials were removed for each participant.
 There was no influence of Cue Type on the percentage of trials removed, as shown with a one-way ANOVA (`r papaja::apa_print.aov(TR_ANOVA)$full_result$variable`).
 An equivilant Bayesian ANOVA showed evidence for the null (BF~10~ = `r round(extractBF(BF_TR_ANOVA)[[1]],3)`).
+-->
   Time freqeucny transform was undertaken closely following the advice of Cohen (2014; *check refrence*).
@@
 Plots <- list()
-RT_comp_xvals <- c("Target","CueType","Distractor","Condition")
-RT_comp_groupvals <- c("Accuracy","Target","CueType","Distractor","Condition")
+RT_comp_xvals <- c("Target","CueType","Distractor")
+RT_comp_groupvals <- c("Accuracy","Target","CueType","Distractor")
 
@@
 }
+
+Plots[[RT_comp_xvals[i]]] <- lapply(RT_comp_groupvals,function(x) RT_RainPlot(data = Trialdata[Trialdata$Rec_pain==1,],
+                                                                      xval = "Condition",
+                                                                      groupval = x))
+names(Plots[[RT_comp_xvals[i]]]) <- RT_comp_groupvals
+
 save(Plots,file = "Output/RT_Rainplots.RData")
@@
 Error_comp_xvals <- "Accuracy"
-Error_comp_groupvals <- c("Target","CueType","Distractor","Condition")
+Error_comp_groupvals <- c("Target","CueType","Distractor")
 
@@
 
+Err_Plots[["Condition"]] <- lapply(Error_comp_groupvals, function(x)
+  Err_RainPlot(
+  data = N_Trials[[x]][N_Trials[[x]]$PartID %in% PainCodes$Subjidx,],
+  xval = "Accuracy",
+  groupval = x
+  ))
+
   save(Err_Plots, file = "Output/Errors_Rainplots.RData")
@@
   reshape2::dcast(
-    data = Trialdata,
+    data = Trialdata %>% dplyr::filter(Accuracy!="Miss"),
     formula = PartID ~ Condition + CueType + Target + Distractor + Accuracy,
@@
 ## Create SPSS/JASP ready dataframe for errors
-N_Trials[["CueType"]]$CueType <- paste(N_Trials[["CueType"]]$CueType,"Cue",sep="")
-N_Trials[["Condition"]]$Condition <- as.character(N_Trials[["Condition"]]$Condition)
-N_Trials[["Distractor"]]$Distractor <- as.character(N_Trials[["Distractor"]]$Distractor)
-N_Trials[["Target"]]$Target <- as.character(N_Trials[["Target"]]$Target)
-
-for (i in seq_along(N_Trials)){
-  names(N_Trials[[i]]) <- c("PartID","Variable","Accuracy","Perc")
-}
-
-## Way too difficult way to create data frame
-Errorsdata <- data.frame(PartID = c(as.character(N_Trials$Condition$PartID),
-                                    as.character(N_Trials$CueType$PartID),
-                                    as.character(N_Trials$Distractor$PartID),
-                                    as.character(N_Trials$Target$PartID)),
-                         Variable = c(as.character(N_Trials$Condition$Variable),
-                                    as.character(N_Trials$CueType$Variable),
-                                    as.character(N_Trials$Distractor$Variable),
-                                    as.character(N_Trials$Target$Variable)),
-                         Accuracy = c(as.character(N_Trials$Condition$Accuracy),
-                                    as.character(N_Trials$CueType$Accuracy),
-                                    as.character(N_Trials$Distractor$Accuracy),
-                                    as.character(N_Trials$Target$Accuracy)),
-                         Perc = c(N_Trials$Condition$Perc,
-                                    N_Trials$CueType$Perc,
-                                    N_Trials$Distractor$Perc,
-                                    N_Trials$Target$Perc)
-                         )
+# Errors
+totalErrors <- Trialdata %>% dplyr::group_by(PartID, Condition, CueType, Target, Distractor, Accuracy) %>% dplyr::tally() %>% dplyr::group_by(PartID, Condition, CueType, Target, Distractor) %>% dplyr::mutate(total = sum(n)) %>% dplyr::mutate(perc = (n/total)*100) %>% dplyr::select(-n,-total) %>% dplyr::filter(Accuracy!="Correct")
+
+ProgramdataErr <-
+  reshape2::dcast(
+    data = totalErrors,
+    formula = PartID ~ Condition + CueType + Target + Distractor + Accuracy,
+    fun.aggregate = mean,
+    value.var = "perc"
+)
+
+# Write to file
+write.csv(ProgramdataErr, file = "Output/Wide_Errdata.csv",
+          row.names = F)
 
@@
 ## 3.1. Behavioural Results
+Table 1 summarises the behavioural data of the C-MAT task used here in both the pain and no pain conditions. Below is the analysis broken down by target modality, cue type, and distractor presence.
+
 ```{r Table 1, echo=FALSE}
@@
 RT_means[["Correct"]][[i]] <- Trialdata %>%
-    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::filter(Accuracy == "Correct",
+                  Rec_pain == 1) %>%
     dplyr::group_by(PartID, get(i), Condition) %>%
@@
 RT_means[["Error"]][[i]] <- Trialdata %>%
-    dplyr::filter(Accuracy == "Error") %>%
+    dplyr::filter(Accuracy == "Error",
+                  Rec_pain == 1) %>%
     dplyr::group_by(PartID, get(i), Condition) %>%
@@
 Error_means[["Error"]][[i]] <- Trialdata %>% 
+  dplyr::filter(Rec_pain == 1) %>%
   dplyr::group_by(PartID, get(i), Accuracy, Condition) %>% 
@@
 Error_means[["Miss"]][[i]] <- Trialdata %>%
+  dplyr::filter(Rec_pain == 1) %>%
   dplyr::group_by(PartID, get(i), Accuracy, Condition) %>%
@@
   dplyr::mutate(total = sum(n)) %>%
-  dplyr::mutate(perc = (n /total) * 100) %>% 
-  dplyr::select(-n, -total) %>% 
-  dplyr::filter(Accuracy =="Miss") %>% 
-  dplyr::group_by(`get(i)`,Condition) %>% 
-  dplyr::summarise(Errors = mean(perc, na.rm=T),
-                   SD = sd(perc,na.rm = T)) %>% 
+  dplyr::mutate(perc = (n / total) * 100) %>%
+  dplyr::select(-n,-total) %>%
+  dplyr::filter(Accuracy == "Miss") %>%
+  dplyr::group_by(`get(i)`, Condition) %>%
+  dplyr::summarise(Errors = mean(perc, na.rm = T),
+  SD = sd(perc, na.rm = T)) %>%
   dplyr::ungroup()
@@
                       .id = "Effect")
-Tab1_RT <- cbind(RT_means$Correct[RT_means$Correct])
+Tab1_RT$RT <- paste(round(Tab1_RT$RT,2)," (",round(Tab1_RT$SD,2),")",sep="")
+Tab1_RT$SD <- NULL
+Tab1_RT <- Tab1_RT %>% tidyr::spread(Condition,RT)
+
 Tab1_RTerr <- dplyr::bind_rows(RT_means$Error,
                       .id = "Effect")
+Tab1_RTerr$`Error RT` <- paste(round(Tab1_RTerr$`Error RT`,2)," (",round(Tab1_RTerr$SD,2),")",sep="")
+Tab1_RTerr$SD <- NULL
+Tab1_RTerr <- Tab1_RTerr %>% tidyr::spread(Condition,`Error RT`)
+
 Tab1_Err <- dplyr::bind_rows(Error_means$Error,
                       .id = "Effect")
+Tab1_Err$`Errors (%)` <- paste(round(Tab1_Err$`Errors (%)`,2)," (",round(Tab1_Err$SD,2),")",sep="")
+Tab1_Err$SD <- NULL
+Tab1_Err <- Tab1_Err %>% tidyr::spread(Condition,`Errors (%)`)
+
 Tab1_Miss <- dplyr::bind_rows(Error_means$Miss,
                       .id = "Effect")
-
-np_Tab1 <- cbind(Tab1_RT[Tab1_RT$Condition=="No Pain",],
-                 Tab1_RTerr[Tab1_RTerr$Condition=="No Pain",][c("Error RT", "SD")],
-                 Tab1_Err[Tab1_Err$Condition=="No Pain",][c("Errors (%)", "SD")],
-                 Tab1_Miss[Tab1_Miss$Condition=="No Pain",][c("Omissions (%)", "SD")]
-)
-np_Tab1$Condition <- NULL
-np_Tab1$Effect <- NULL
-
-p_Tab1 <- cbind(Tab1_RT[Tab1_RT$Condition=="Pain",],
-                 Tab1_RTerr[Tab1_RTerr$Condition=="Pain",][c("Error RT", "SD")],
-                 Tab1_Err[Tab1_Err$Condition=="Pain",][c("Errors (%)", "SD")],
-                 Tab1_Miss[Tab1_Miss$Condition=="Pain",][c("Omissions (%)", "SD")]
-)
-p_Tab1$Condition <- NULL
-p_Tab1$Effect <- NULL
-
-Table1 <- cbind(np_Tab1,p_Tab1)
-names(Table1) <-
-  c(
-  "",
-  "RT",
-  "SD",
-  "Error RT",
-  "SD",
-  "Errors (%)",
-  "SD",
-  "Omissions (%)",
-  "SD",
-  "Variable",
-  "RT",
-  "SD",
-  "Error RT",
-  "SD",
-  "Errors (%)",
-  "SD",
-  "Omissions (%)",
-  "SD"
-  )
-Table1$Variable <- NULL
-
-# Paste the SD with the RT in brackets? - round to 2 digits
+Tab1_Miss$`Omissions (%)` <- paste(round(Tab1_Miss$`Omissions (%)`,2)," (",round(Tab1_Miss$SD,2),")",sep="")
+Tab1_Miss$SD <- NULL
+Tab1_Miss <- Tab1_Miss %>% tidyr::spread(Condition,`Omissions (%)`)
+
+## Bring tables together into table, dropping the effect and variable columns
+
+Table1 <- cbind(Tab1_RT %>% select(-Effect),
+                Tab1_RTerr %>% select(-Effect,-Variable),
+                Tab1_Err %>% select(-Effect,-Variable),
+                Tab1_Miss %>% select(-Effect,-Variable))
+
+names(Table1)[names(Table1) == 'Variable'] <- ' '
 
@@
 # Row Groupings for Modality, Cue Type, Distractor
-kable(Table1, caption = "Table 1. Behavoural Summary Stats",digits = 2) %>%
+kable(Table1, caption = "Table 1. Summary of the behavioural data for the no pain and pain conditions, split by the cue type, distractor presence, and target modality.") %>%
   kable_styling("striped", full_width = F) %>%
- add_header_above(c(" " = 1, "No Pain" = 8, "Pain" = 8)) %>% 
-  pack_rows("Modality", 1, 2) %>%
-  pack_rows("Cue Type", 3, 5) %>% 
-  pack_rows("Distractor",6, 7)
-
-```
+ add_header_above(c(" ", "Correct RT (ms)" = 2, "Error RT (ms)" = 2, "Errors (%)" = 2, "Omissions (%)" = 2)) %>% 
+  pack_rows("Cue Type", 1, 2) %>%
+  pack_rows("Distractor", 3, 4) %>% 
+  pack_rows("Modality", 5, 6) %>%
+column_spec(1, bold = T, border_right = T) %>% 
+  footnote(general = "Data are presented as the mean (standard deviation)."
+)
+
+write.csv(Table1,
+          file = "Output/Table1.csv",
+          row.names = T)
+
+```
+
+```{r ANOVA}
+## Run ANOVAs on each effect; Preparation, Distraction, Modality
+
+## Correct RT
+# Test interaction effects.
+ANOVAtest <- list()
+
+## Full model
+ANOVAtest[["Full"]] <- BayesFactor::lmBF(
+    formula = RT ~ Target * CueType * Distractor * Condition + PartID,
+    data = Trialdata %>%
+      dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+      dplyr::group_by(PartID, Target, CueType, Distractor, Condition) %>%
+      dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID"
+  )
+
+ANOVAtest[["MainEff"]] <- BayesFactor::lmBF(
+    formula = RT ~ Target + CueType + Distractor + Condition + PartID,
+    data = Trialdata %>%
+      dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+      dplyr::group_by(PartID, Target, CueType, Distractor, Condition) %>%
+      dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID"
+  )
+
+# Support for just the main effects compared to the interactions
+ANOVAtest[["MainEff"]]/ANOVAtest[["MainEff"]]
+
+## Now build models for each main effect to compare against 
+ANOVAtest[["Null"]] <- BayesFactor::lmBF(
+    formula = RT ~ 1 + PartID,
+    data = Trialdata %>%
+      dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+      dplyr::group_by(PartID, Target, CueType, Distractor, Condition) %>%
+      dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID"
+  )
+
+ANOVAtest[["Condition"]] <- BayesFactor::lmBF(
+    formula = RT ~ Condition + PartID,
+    data = Trialdata %>%
+      dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+      dplyr::group_by(PartID, Target, CueType, Distractor, Condition) %>%
+      dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID"
+  )
+
+ANOVAtest[["Target"]] <- BayesFactor::lmBF(
+    formula = RT ~ Target + PartID,
+    data = Trialdata %>%
+      dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+      dplyr::group_by(PartID, Target, CueType, Distractor, Condition) %>%
+      dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID"
+  )
+
+ANOVAtest[["CueType"]] <- BayesFactor::lmBF(
+    formula = RT ~ CueType + PartID,
+    data = Trialdata %>%
+      dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+      dplyr::group_by(PartID, Target, CueType, Distractor, Condition) %>%
+      dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID"
+  )
+
+ANOVAtest[["Distractor"]] <- BayesFactor::lmBF(
+    formula = RT ~ Distractor + PartID,
+    data = Trialdata %>%
+      dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+      dplyr::group_by(PartID, Target, CueType, Distractor, Condition) %>%
+      dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID"
+  )
+
+incmods <- bayestestR::bayesfactor_models(
+  ANOVAtest[["Condition"]],ANOVAtest[["Target"]],ANOVAtest[["CueType"]],ANOVAtest[["Distractor"]],ANOVAtest$MainEff,ANOVAtest$Full,
+  denominator =  ANOVAtest[["Null"]])
+
+bayestestR::bayesfactor_inclusion(
+  incmods,
+  match_models = F
+)
+
+InteractionTests[["Full"]][["Inclusion"]] <- bayestestR::bayesfactor_inclusion(
+  InteractionTests[["Full"]][["ANOVA"]],
+  match_models = T
+)
+
+## Error Test
+full <- BayesFactor::anovaBF(
+  formula = perc ~ Target * CueType * Distractor * Condition + PartID,
+  data = Trialdata %>%
+    dplyr::group_by(PartID, Condition, CueType, Target, Distractor, Accuracy) %>%
+    dplyr::tally() %>%
+    dplyr::group_by(PartID, Condition, CueType, Target, Distractor) %>%
+    dplyr::mutate(total = sum(n)) %>%
+    dplyr::mutate(perc = (n / total) * 100) %>%
+    dplyr::select(-n,-total) %>%
+    dplyr::filter(Accuracy == "Error") %>%
+    dplyr::select(-Accuracy),
+  whichRandom = "PartID",
+  iterations = 1000
+)
+
+bayestestR::bayesfactor_inclusion(
+full,  match_models = F
+)
+
+full <- BayesFactor::anovaBF(
+  formula = perc ~ Target * CueType * Distractor * Condition + PartID,
+  data = Trialdata %>%
+    dplyr::group_by(PartID, Condition, CueType, Target, Distractor, Accuracy) %>%
+    dplyr::tally() %>%
+    dplyr::group_by(PartID, Condition, CueType, Target, Distractor) %>%
+    dplyr::mutate(total = sum(n)) %>%
+    dplyr::mutate(perc = (n / total) * 100) %>%
+    dplyr::select(-n,-total) %>%
+    dplyr::filter(Accuracy == "Miss") %>%
+    dplyr::select(-Accuracy),
+  whichRandom = "PartID",
+  iterations = 1000
+)
+
+bayestestR::bayesfactor_inclusion(
+full,  match_models = F
+)
+
+# papaja::apa_print.BFBayesFactor(InteractionTests[["Full"]][["ANOVA"]])
+
+## Follow-up Bayes t-tests
+BayesT <- list(Modality = list(),
+  Preparation = list(),
+  Distractor = list(),
+  Condition = list()
+)
+
+BayesT[["Preparation"]] <- 
+    BayesFactor::ttestBF(
+      x = Trialdata %>%
+        dplyr::filter(Accuracy == "Correct",
+                      Rec_pain == 1) %>%
+        dplyr::group_by(PartID, CueType) %>%
+        dplyr::summarise(RT = mean(RT, na.rm = T)) %>%
+        tidyr::spread(CueType, RT) %>% .$Ambiguous,
+      y = Trialdata %>%
+        dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+        dplyr::group_by(PartID, CueType) %>%
+        dplyr::summarise(RT = mean(RT, na.rm = T)) %>%
+        tidyr::spread(CueType, RT) %>% .$Cued,
+      paired = T)
+
+BayesT[["Modality"]] <-
+    BayesFactor::ttestBF(
+      x = Trialdata %>%
+        dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+        dplyr::group_by(PartID, Target) %>%
+        dplyr::summarise(RT = mean(RT, na.rm = T)) %>%
+        tidyr::spread(Target, RT) %>% .$Visual,
+      y = Trialdata %>%
+        dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+        dplyr::group_by(PartID, Target) %>%
+        dplyr::summarise(RT = mean(RT, na.rm = T)) %>%
+        tidyr::spread(Target, RT) %>% .$Auditory,
+      paired = T)
+
+BayesT[["Distractor"]] <-
+    BayesFactor::ttestBF(
+      x = Trialdata %>%
+        dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+        dplyr::group_by(PartID, Distractor) %>%
+        dplyr::summarise(RT = mean(RT, na.rm = T)) %>%
+        tidyr::spread(Distractor, RT) %>% .$Absent,
+      y = Trialdata %>%
+        dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+        dplyr::group_by(PartID, Distractor) %>%
+        dplyr::summarise(RT = mean(RT, na.rm = T)) %>%
+        tidyr::spread(Distractor, RT) %>% .$Present,
+      paired = T)
+
+BayesT[["Condition"]] <-
+    BayesFactor::ttestBF(
+      x = Trialdata %>%
+        dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+        dplyr::group_by(PartID, Condition) %>%
+        dplyr::summarise(RT = mean(RT, na.rm = T)) %>%
+        tidyr::spread(Condition, RT) %>% .$`No Pain`,
+      y = Trialdata %>%
+        dplyr::filter(Accuracy == "Correct",
+                    Rec_pain == 1) %>%
+        dplyr::group_by(PartID, Condition) %>%
+        dplyr::summarise(RT = mean(RT, na.rm = T)) %>%
+        tidyr::spread(Condition, RT) %>% .$Pain,
+      paired = T)
+
+## Post-hoc t-test to confirm effect of pain
+BayesT[["Modality"]][["Pain"]] <-
+  sapply(c("Visual", "Auditory"), function(i)
+    BayesFactor::ttestBF(
+      x = Trialdata %>%
+        dplyr::filter(Accuracy == "Correct",
+                      Target == i,
+                    Rec_pain == 1) %>%
+        dplyr::group_by(PartID, Condition) %>%
+        dplyr::summarise(RT = mean(RT, na.rm = T)) %>%
+        tidyr::spread(Condition, RT) %>% .$`No Pain`,
+      y = Trialdata %>%
+        dplyr::filter(Accuracy == "Correct",
+                      Target == i,
+                    Rec_pain == 1) %>%
+        dplyr::group_by(PartID, Condition) %>%
+        dplyr::summarise(RT = mean(RT, na.rm = T)) %>%
+        tidyr::spread(Condition, RT) %>% .$Pain,
+      paired = T
+    ), USE.NAMES = T)
+
+BayesT[["Distractor"]] <-
+  sapply(c("No Pain", "Pain"), function(i)
+    BayesFactor::ttestBF(
+      x = Trialdata %>%
+        dplyr::filter(Accuracy == "Correct",
+                      Condition == i,
+                    Rec_pain == 1) %>%
+        dplyr::group_by(PartID, Distractor) %>%
+        dplyr::summarise(RT = mean(RT, na.rm = T)) %>%
+        tidyr::spread(Distractor, RT) %>% .$Absent,
+      y = Trialdata %>%
+        dplyr::filter(Accuracy == "Correct",
+                      Condition == i,
+                    Rec_pain == 1) %>%
+        dplyr::group_by(PartID, Distractor) %>%
+        dplyr::summarise(RT = mean(RT, na.rm = T)) %>%
+        tidyr::spread(Distractor, RT) %>% .$Present,
+      paired = T
+    ), USE.NAMES = T)
+
+```
+
+  In the full ANOVA model there was evidence to support each main effect, seperately.
+
+```{r Plotting Results}
+## Preparation Effect
+Plotdata <- list()
+
+Plotdata[["PreparationCOND"]] <- Trialdata %>%
+  dplyr::filter(Accuracy == "Correct",
+                Rec_pain == 0) %>% # This is necessary across all RT data - Hard coded!
+  dplyr::group_by(PartID, CueType, Condition) %>%
+  dplyr::summarise(RT = mean(RT, na.rm = T))
+
+Plotdata[["DistractionCOND"]] <- Trialdata %>%
+  dplyr::filter(Accuracy == "Correct",
+                Rec_pain == 0,
+                CueType == "Cued",
+                Target == "Visual") %>% 
+  dplyr::group_by(PartID, Distractor, Condition) %>%
+  dplyr::summarise(RT = mean(RT, na.rm = T))
+
+wse <- list()
+wse[["PreparationCOND"]] <- Rmisc::summarySEwithin(
+  Plotdata[["PreparationCOND"]],
+  measurevar = "RT",
+  withinvars = c("CueType","Condition"),
+  idvar = "PartID",
+  na.rm = T,
+  conf.interval = .95
+)
+
+wse[["DistractionCOND"]] <- Rmisc::summarySEwithin(
+  Plotdata[["DistractionCOND"]],
+  measurevar = "RT",
+  withinvars = c("Distractor","Condition"),
+  idvar = "PartID",
+  na.rm = T,
+  conf.interval = .95
+)
+
+w = 16
+h = 4
+
+# ## Make and save plot
+# ggplot(Plotdata[["PreparationCOND"]], aes(x = CueType, y = RT, fill = Condition)) +
+#       geom_boxplot(
+#       aes(x = CueType, y = RT, fill = Condition),
+#       outlier.shape = NA,
+#       alpha = .5,
+#       width = .1,
+#       colour = "black"
+#     ) +
+#     geom_point(
+#       aes(
+#         x = as.numeric(CueType) -.15,
+#         y = RT,
+#         colour = Condition
+#       ),
+#       position = position_jitter(width = .05),
+#       size = 1.5,
+#       shape = 20
+#     ) +
+#     geom_point(
+#       data = wse[["PreparationCOND"]],
+#       aes(
+#         x = as.numeric(CueType) -.15,
+#         y = RT,
+#         group = Condition,
+#         colour = Condition
+#       ),
+#       shape = 18,
+#       size = 3
+#     ) +
+#   geom_line(data = wse[["PreparationCOND"]],
+#       aes(x = as.numeric(CueType) -.15,
+#         y = RT,
+#         group = Condition,
+#         colour = Condition))+
+#     geom_errorbar(
+#       data = wse[["PreparationCOND"]],
+#       aes(
+#         x = as.numeric(CueType) -.15,
+#         y = RT,
+#         group = Condition,
+#         colour = Condition,
+#         ymin = RT - se,
+#         ymax = RT + se
+#       ),
+#       width = .05
+#     ) +
+#     scale_colour_manual(values = wes_palette("GrandBudapest1")) + # Change to colour blind friendly for publication
+#     scale_fill_manual(values = wes_palette("GrandBudapest1")) +
+#     theme_classic() +
+#     theme(legend.position = c(.9, .2)) +
+#     ggsave(
+#       paste("Output/Plots/PreparationCOND.tiff", sep = ""),
+#       width = w,
+#       height = h)
+
+ggplot(Plotdata[["DistractionCOND"]], aes(x = Distractor, y = RT, fill = Condition)) +
+  geom_boxplot(
+    aes(x = Distractor, y = RT, fill = Condition),
+    outlier.shape = NA,
+    alpha = .5,
+    width = .1,
+    colour = "black"
+  ) +
+  geom_point(
+    aes(
+      x = as.numeric(Distractor) - .15,
+      y = RT,
+      colour = Condition
+    ),
+    position = position_jitter(width = .05),
+    size = 1.5,
+    shape = 20
+  ) +
+  geom_point(
+    data = wse[["DistractionCOND"]],
+    aes(
+      x = as.numeric(Distractor) - .15,
+      y = RT,
+      group = Condition,
+      colour = Condition
+    ),
+    shape = 18,
+    size = 3
+  ) +
+  geom_line(data = wse[["DistractionCOND"]],
+            aes(
+              x = as.numeric(Distractor) - .15,
+              y = RT,
+              group = Condition,
+              colour = Condition
+            )) +
+  geom_errorbar(
+    data = wse[["DistractionCOND"]],
+    aes(
+      x = as.numeric(Distractor) - .15,
+      y = RT,
+      group = Condition,
+      colour = Condition,
+      ymin = RT - se,
+      ymax = RT + se
+    ),
+    width = .05
+  ) +
+  scale_colour_manual(values = wes_palette("GrandBudapest1")) + # Change to colour blind friendly for publication
+  scale_fill_manual(values = wes_palette("GrandBudapest1")) +
+  theme_classic() +
+  theme(legend.position = c(.9, .2)) +
+  ggsave("Output/Plots/DistractionCOND.png")
+
+```
+
+```{r ANOVA - Cue Type}
+
+BayesT <- list()
+
+BayesT[["CueTypeCondition"]] <- Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)) %>% 
+    tidyr::unite(Effect,Condition,CueType) %>% 
+    tidyr::spread(Effect,RT)
+
+write.csv(BayesT$CueTypeCondition,
+          file = "Output/CueTypeCond.csv")
+
+BayesT[["TargetCondition"]] <- Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, Target, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)) %>% 
+    tidyr::unite(Effect,Condition,Target) %>% 
+    tidyr::spread(Effect,RT)
+
+write.csv(BayesT$TargetCondition,
+          file = "Output/TargetCond.csv")
+
+BayesT[["DistractorCondition"]] <- Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)) %>% 
+    tidyr::unite(Effect,Condition,Distractor) %>% 
+    tidyr::spread(Effect,RT)
+
+write.csv(BayesT$DistractorCondition,
+          file = "Output/DistractorCond.csv")
+
+ProgramData <- dplyr::bind_cols(BayesT)
+
+# No pain Preparation (CueType) Effect
+ProgramData$np_PreparationEff <- ProgramData$`No Pain_Ambiguous`- ProgramData$`No Pain_Cued`
+
+# No pain Target Effect
+ProgramData$np_TargetEff <- ProgramData$`No Pain_Auditory`- ProgramData$`No Pain_Visual`
+
+# No pain Distraction Effect
+ProgramData$np_DistractionEff <- ProgramData$`No Pain_Present`- ProgramData$`No Pain_Absent`
+
+# Pain Preparation (CueType) Effect
+ProgramData$p_PreparationEff <- ProgramData$Pain_Ambiguous- ProgramData$Pain_Cued
+
+# Pain Target Effect
+ProgramData$p_TargetEff <- ProgramData$Pain_Auditory- ProgramData$Pain_Visual
+
+# Pain Distraction Effect
+ProgramData$p_DistractionEff <- ProgramData$Pain_Present- ProgramData$Pain_Absent
+
+write.csv(ProgramData,
+          file = "Output/TtestData.csv")
+
+BayesModels <- list()
+
+# BayesModels[["Null"]] <-
+#   BayesFactor::lmBF(
+#     RT ~ PartID,
+#     data = Trialdata %>%
+#     dplyr::filter(Accuracy == "Correct") %>%
+#     dplyr::group_by(PartID) %>%
+#     dplyr::summarise(RT = mean(RT, na.rm = T)),
+#     whichRandom = "PartID",
+#     progress = F,
+#     iterations = 10000,posterior = F)
+
+## Cue Type
+BayesModels[["CueType"]] <-
+  BayesFactor::lmBF(
+    RT ~ CueType  + PartID,
+    data = Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Target, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID",
+    progress = F,
+    iterations = 10000,posterior = F)
+BayesModels[["CueTypeCondition"]] <-
+  BayesFactor::lmBF(
+    RT ~ CueType + Condition + PartID,
+    data = Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Target, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID",
+    progress = F,
+    iterations = 10000,posterior = F)
+
+BayesModels[["CueTypeConditionInt"]] <-
+  BayesFactor::lmBF(
+    RT ~ CueType * Condition + PartID,
+    data = Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Target, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID",
+    progress = F,
+    iterations = 10000,posterior = F)
+
+## Target
+BayesModels[["Target"]] <-
+  BayesFactor::lmBF(
+    RT ~ Target  + PartID,
+    data = Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Target, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID",
+    progress = F,
+    iterations = 10000,posterior = F)
+
+BayesModels[["TargetCondition"]] <-
+  BayesFactor::lmBF(
+    RT ~ Target + Condition + PartID,
+    data = Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Target, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID",
+    progress = F,
+    iterations = 10000,posterior = F)
+
+BayesModels[["TargetConditionInt"]] <-
+  BayesFactor::lmBF(
+    RT ~ Target * Condition + PartID,
+    data = Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Target, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID",
+    progress = F,
+    iterations = 10000,posterior = F)
+
+## Distractor
+BayesModels[["Distractor"]] <-
+  BayesFactor::lmBF(
+    RT ~ Distractor  + PartID,
+    data = Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Target, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID",
+    progress = F,
+    iterations = 10000,posterior = F)
+
+BayesModels[["DistractorCondition"]] <-
+  BayesFactor::lmBF(
+    RT ~ Distractor + Condition + PartID,
+    data = Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Target, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID",
+    progress = F,
+    iterations = 10000,posterior = F)
+
+BayesModels[["DistractorConditionInt"]] <-
+  BayesFactor::lmBF(
+    RT ~ Distractor * Condition + PartID,
+    data = Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Target, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID",
+    progress = F,
+    iterations = 10000,posterior = F)
+
+## Condition
+BayesModels[["Condition"]] <-
+  BayesFactor::lmBF(
+    RT ~ Condition + PartID,
+    data = Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Target, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID",
+    progress = F,
+    iterations = 10000,posterior = F)
+
+## Full Main Effects
+BayesModels[["Full"]] <-
+  BayesFactor::lmBF(
+    RT ~ CueType + Target + Distractor + Condition + PartID,
+    data = Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Target, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID",
+    progress = F,
+    iterations = 10000,posterior = F)
+
+## Full Interactions
+BayesModels[["FullInt"]] <-
+  BayesFactor::lmBF(
+    RT ~ CueType * Target * Distractor * Condition + PartID,
+    data = Trialdata %>%
+    dplyr::filter(Accuracy == "Correct") %>%
+    dplyr::group_by(PartID, CueType, Target, Distractor, Condition) %>%
+    dplyr::summarise(RT = mean(RT, na.rm = T)),
+    whichRandom = "PartID",
+    progress = F,
+    iterations = 10000,posterior = F)
+
+# Compare models - Build them up some simple effects, to combined, to interaction
+mods <- bayestestR::bayesfactor_models(BayesModels$CueType,
+                                       BayesModels$Condition,
+                                       BayesModels$Target,
+                                       BayesModels$Distractor)
+# BF inclusion
+bayestestR::bayesfactor_inclusion(mods,match_models = T)
+```
+
+The effect of preparation on correct RT was assessed with a Bayesian two-way ANOVA of Cue Type (Ambiguous vs Cued) and Condition (No Pain vs Pain).
+Results suggested that there was evidence in favour of the effect of cueing ($BF$~10~ $=$ `r extractBF(BayesModels[["CueType"]],onlybf = T,logbf = F)`).
+
+Visual cues provided the fastest responses, faster than both Auditory ($BF$~10~ $=$ `r extractBF(Bayesposthoc[["VisAud"]],onlybf = T,logbf = F)`) and Ambiguous ($BF$~10~ $=$ `r extractBF(Bayesposthoc[["VisAmb"]],onlybf = T,logbf = F)`).
+Interestingly, Ambiguous cues were also found to be faster than
+followed by Ambiguous cues, and finally Auditory cues. This order was consistient across pain conditions, where RT remained relatively equal.
 

### 2020-08-28 Functions/ExtractRT_MATLAB.R

@@ -1,13 +1,15 @@
-ExtractTrialData <- function(PartID,COND){
+ExtractTrialData <- function(PartID,COND,dataloc = "../Data/"){
 
 ## Code to extract RT values from MATLAB event structures
-
+if (file.exists(paste(dataloc,PartID,"/Behaviour/",
+                     paste(PartID,COND,sep = "_"),
+                     "_EventCodes.mat",sep = ""))){
 require(rmatio)
 require(dplyr)
 
 ## Import Data
 mat <-
-  rmatio::read.mat(paste("../Data/",PartID,"/Behavior/",
+  rmatio::read.mat(paste(dataloc,PartID,"/Behaviour/",
                          paste(PartID,COND,sep = "_"),
                          "_EventCodes.mat",sep = ""))
 
@@ -267,7 +269,7 @@ CTIlist <- list()
 for (i in seq_along(TrialList)) {
   CTIlist[[i]] <-
     (TrialList[[i]] %>% dplyr::filter(Trig %in% TOI$Target) %>% .$Lat) - (TrialList[[i]] %>% dplyr::filter(Trig %in% TOI$Stim) %>% .$Lat)
-  if (length(CTIlist[[i]]) > 1) {
+  if (length(CTIlist[[i]]) > 1 | length(CTIlist[[i]]) < 1) {
     CTIlist[[i]] <- NA
   }
 }
@@ -279,7 +281,7 @@ ITIlist <- list()
 for (i in 1:(length(TrialList)-1)) {
   ITIlist[[i]] <-
     (TrialList[[i+1]] %>% dplyr::filter(Trig %in% TOI$Stim) %>% .$Lat) - (TrialList[[i]] %>% dplyr::filter(Trig %in% TOI$Stim) %>% .$Lat)
-  if (length(ITIlist[[i]]) > 1) {
+  if (length(ITIlist[[i]]) > 1 | length(ITIlist[[i]]) < 1) {
     ITIlist[[i]] <- NA
   }
 }
@@ -297,12 +299,16 @@ Trialdata <- Trialdata %>% dplyr::select(PartID,TrialNum,CueType,
 
 #### Write Trialdata to file ####
 write.csv(Trialdata,row.names = F,
-          file = paste("../Data/",PartID,"/Behavior/",
+          file = paste(dataloc,PartID,"/Behaviour/",
                        paste(PartID,COND,sep = "_"),
                        "_TrialData.csv",sep = ""))
 
[…]

### 2020-08-28 Functions/MethodsList.R

@@ -120,6 +120,7 @@ MethodsList <- function(data) {
       minITI = min(ITI,na.rm = T),
       maxITI = max(ITI,na.rm =T)
     )
+  
   # Rates of each trial type
   # Create dummy variable of total N_trials per condtion, per participant
   Summdata$Total_Trials <- NA # Create variable
